### 2024-08-27 draft_1.qmd
first draft

---
title: "Title"
format: #docx
    tandf-pdf:
      keep-tex: true  
    tandf-html: default
author:
  - name: Sultana Mubarika Rahman Chowdhury
    affiliations:
      - ref: biostat
    orcid: 
    email: schow034@fiu.edu
  - name: B.M Golam Kibria
    affiliations:
      - ref: stat
affiliations:
  - id: biostat
    name: Florida International University
    department: Biosatistics Department
    address: FIU
    city: Miami, Fl
    country: USA
    postal-code: 13210
  - id: stat
    name: Florida International University
    department: Department of Mathematics and Statistics
    address: FIU
    city: Miami, Fl
    country: USA
    postal-code: 13210
abstract: |
  Write down the abstract here
keywords: 
  - Ridge Regression
  - Multicolinearity
bibliography: bibliography.bib  
---

# Introduction

# Ridge Regression

# Simulation Study

# Application

# Discussion and Conclusion

### 2024-08-27 draft_1.tex
first draft

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{interact}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{orcidlink}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Title},
  pdfauthor={Sultana Mubarika Rahman Chowdhury; B.M Golam Kibria},
  pdfkeywords={Ridge Regression, Multicolinearity},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Title}
\author{Sultana Mubarika Rahman Chowdhury$\textsuperscript{1}$, B.M
Golam Kibria$\textsuperscript{2}$}

\thanks{CONTACT: Sultana Mubarika Rahman
Chowdhury. Email: \href{mailto:schow034@fiu.edu}{\nolinkurl{schow034@fiu.edu}}. }
\begin{document}
\captionsetup{labelsep=space}
\maketitle
\textsuperscript{1} Biosatistics Department, Florida International
University, Miami, Fl, USA\\ \textsuperscript{2} Department of
Mathematics and Statistics, Florida International University, Miami,
Fl, USA
\begin{abstract}
Write down the abstract here
\end{abstract}
\begin{keywords}
\def\sep{;\ }
Ridge Regression\sep 
Multicolinearity
\end{keywords}

\section{Introduction}\label{introduction}

\section{Ridge Regression}\label{ridge-regression}

\section{Simulation Study}\label{simulation-study}

\section{Application}\label{application}

\section{Discussion and Conclusion}\label{discussion-and-conclusion}

\end{document}

### 2024-08-27 draft_1.qmd
first draft

@@
 ---
-title: "Title"
+title: "Comparison of Confidence Interval in the OLS and Ridge Linear Regression Model: A Comparative study via Simulation"
 format: #docx
@@
       - ref: stat
+  - name: Zoran Bursac
+    affiliations:
+      - ref: biostat
 affiliations:
@@
     department: Biosatistics Department
-    address: FIU
+    address: 11200 SW 8th St
     city: Miami, Fl
     country: USA
-    postal-code: 13210
+    postal-code: 33199
   - id: stat
@@
     department: Department of Mathematics and Statistics
-    address: FIU
+    address: 11200 SW 8th St 
     city: Miami, Fl
     country: USA
-    postal-code: 13210
+    postal-code: 33199
 abstract: |
@@
 keywords: 
+  - Multiple Linear Regression
   - Ridge Regression
@@
 
-# Ridge Regression
+Multiple linear regression maps the relationship between two or more predictors and dependent variable to a linear equation.
+The aim is to predict the response variable uisng the indepnedent variables.
+If X is a n×p full rank matrix of predictors and Y is a n × 1 vector of response variables the multiple linear regression can be explained as,
+
+$$Y = X \times \beta + \epsilon$$,
+where, $\beta$ is an p × 1 unknown regression paramaters and $\epsilon$ is the n × 1 vector of error with mean zero and equal variance.
+
+One of the key assumption of the widely used multiple linear regression model is that the predictors need to be independent of each other.
+Violating the assumption of independence results in an issue known as multicollinearity.
+Multicollinearity occurs when two or more independent variables are highly correlated with each other.
+It causes standard error of the coefficient to increase resulting in wide confidence interval and less reliable results.
+Identifying significant predictors also becomes difficult.
+
+# Statistical Methodology
+
+## Ridge Regression Estimators
+
+## Confidence Interval
 

### 2024-08-27 draft_1.tex
first draft

@@
 \hypersetup{
-  pdftitle={Title},
-  pdfauthor={Sultana Mubarika Rahman Chowdhury; B.M Golam Kibria},
-  pdfkeywords={Ridge Regression, Multicolinearity},
+  pdftitle={Comparison of Confidence Interval in the OLS and Ridge Linear Regression Model: A Comparative study via Simulation},
+  pdfauthor={Sultana Mubarika Rahman Chowdhury; B.M Golam Kibria; Zoran Bursac},
+  pdfkeywords={Multiple Linear Regression, Ridge
+Regression, Multicolinearity},
   colorlinks=true,
@@
 
-\title{Title}
+\title{Comparison of Confidence Interval in the OLS and Ridge Linear
+Regression Model: A Comparative study via Simulation}
 \author{Sultana Mubarika Rahman Chowdhury$\textsuperscript{1}$, B.M
-Golam Kibria$\textsuperscript{2}$}
+Golam Kibria$\textsuperscript{2}$, Zoran Bursac$\textsuperscript{1}$}
 
@@
 \def\sep{;\ }
-Ridge Regression\sep 
+Multiple Linear Regression\sep Ridge Regression\sep 
 Multicolinearity
@@
 
-\section{Ridge Regression}\label{ridge-regression}
+One of the key assumption of the widely used multiple linear regression
+model is that the predictors need to be independent of each other.
+Violating the assumption of independence results in an issue known as
+multicollinearity. Linear regression maps the relationship between the
+predictors and dependent variable with a linear equation. If X is a n×p
+full rank matrix of predictors and Y is a n × 1 vector of response
+variables the multiple linear regression can be explained as,
+
+\[Y = X \times \beta + \epsilon\], where, \(\beta\) is an p × 1 unknown
+regression paramaters and \[\epsilon\] is the n × 1 vector of error with
+mean zero and equal variance.\\
+\# Statistical Methodology
+
+\subsection{Ridge Regression
+Estimators}\label{ridge-regression-estimators}
 

### 2024-08-28 draft_1.qmd
introduction edit

@@
 Multiple linear regression maps the relationship between two or more predictors and dependent variable to a linear equation.
-The aim is to predict the response variable uisng the indepnedent variables.
+The aim is to predict the response variable using the independent variables.
 If X is a n×p full rank matrix of predictors and Y is a n × 1 vector of response variables the multiple linear regression can be explained as,
 
-$$Y = X \times \beta + \epsilon$$,
-where, $\beta$ is an p × 1 unknown regression paramaters and $\epsilon$ is the n × 1 vector of error with mean zero and equal variance.
+$$Y = X \times \beta + \epsilon, $$
+where, $\beta$ is an p × 1 unknown regression paramaters and $\epsilon$ is the n × 1 vector of error with mean zero and equal variance.Ordinary Least Square (OLS) method is commonly used to estimate the unknown regression parameter.
+The OLS estimate in case of linear regression model is defined as follows,
 
-One of the key assumption of the widely used multiple linear regression model is that the predictors need to be independent of each other.
-Violating the assumption of independence results in an issue known as multicollinearity.
+$$\hat{\beta} = (X^T X)^{-1} X^T y.$$
+
+One of the key assumption of the widely used multiple linear regression model is that the predictors need to be independent of each other. Violating the assumption of independence 
+results in an issue known as multicollinearity.
 Multicollinearity occurs when two or more independent variables are highly correlated with each other.
-It causes standard error of the coefficient to increase resulting in wide confidence interval and less reliable results.
-Identifying significant predictors also becomes difficult.
+It causes standard error of the OLS coefficient to increase resulting in wide confidence intervals and less reliable results.
+Identifying and interpreting significant predictors also becomes difficult.
+As the field of study progressed, researchers developed a number of methods to address presence of multicollinearity in data.
+Ridge regression [@hoerl1970ridge], Lasso,
+
+Ridge regression is one of the methods proposed by @hoerl1970ridge that mitigates the effects of multicollinearity by introducing an amount of bias in to the model.
+
+para about differnt techniques,
+
+para about ridge
+
+para about CI
+
+para about Aim
+
+Note:
 
@@
 
+## CI for Ridge regression
+
 # Simulation Study
@@
 # Discussion and Conclusion
+
+# Bibliography

### 2024-08-28 draft_1.tex
introduction edit

@@
 \makeatother
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
+  \fi
+  % set entry spacing
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 
+Multiple linear regression maps the relationship between two or more
+predictors and dependent variable to a linear equation. The aim is to
+predict the response variable using the independent variables. If X is a
+n×p full rank matrix of predictors and Y is a n × 1 vector of response
+variables the multiple linear regression can be explained as,
+
+\[Y = X \times \beta + \epsilon, \] where, \(\beta\) is an p × 1 unknown
+regression paramaters and \(\epsilon\) is the n × 1 vector of error with
+mean zero and equal variance.Ordinary Least Square (OLS) method is
+commonly used to estimate the unknown regression parameter. The OLS
+estimate in case of linear regression model is defined as follows,
+
+\[\hat{\beta} = (X^T X)^{-1} X^T y.\]
+
 One of the key assumption of the widely used multiple linear regression
@@
 Violating the assumption of independence results in an issue known as
-multicollinearity. Linear regression maps the relationship between the
-predictors and dependent variable with a linear equation. If X is a n×p
-full rank matrix of predictors and Y is a n × 1 vector of response
-variables the multiple linear regression can be explained as,
+multicollinearity. Multicollinearity occurs when two or more independent
+variables are highly correlated with each other. It causes standard
+error of the OLS coefficient to increase resulting in wide confidence
+intervals and less reliable results. Identifying and interpreting
+significant predictors also becomes difficult. As the field of study
+progressed, researchers developed a number of methods to address
+presence of multicollinearity in data. Ridge regression (Hoerl and
+Kennard 1970), Lasso,
 
-\[Y = X \times \beta + \epsilon\], where, \(\beta\) is an p × 1 unknown
-regression paramaters and \[\epsilon\] is the n × 1 vector of error with
-mean zero and equal variance.\\
-\# Statistical Methodology
+Ridge regression is one of the methods proposed by Hoerl and Kennard
+(1970) that mitigates the effects of multicollinearity by introducing an
+amount of bias in to the model.
+
+para about differnt techniques,
+
+para about ridge
+
+para about CI
+
+para about Aim
+
+Note:
+
+\section{Statistical Methodology}\label{statistical-methodology}
 
@@
 Estimators}\label{ridge-regression-estimators}
+
+\subsection{Confidence Interval}\label{confidence-interval}
+
+\subsection{CI for Ridge regression}\label{ci-for-ridge-regression}
 
@@
 
+\section*{Bibliography}\label{bibliography}
+\addcontentsline{toc}{section}{Bibliography}
+
+\phantomsection\label{refs}
+\begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-hoerl1970ridge}
+Hoerl, Arthur E, and Robert W Kennard. 1970. {``Ridge Regression: Biased
+Estimation for Nonorthogonal Problems.''} \emph{Technometrics} 12 (1):
+55--67.
+
+\end{CSLReferences}
+
 \end{document}

### 2024-08-29 draft_1.qmd
continued

@@
     email: schow034@fiu.edu
-  - name: B.M Golam Kibria
+  - name: B.M. Golam Kibria
     affiliations:
@@
 
-$$Y = X \times \beta + \epsilon, $$
-where, $\beta$ is an p × 1 unknown regression paramaters and $\epsilon$ is the n × 1 vector of error with mean zero and equal variance.Ordinary Least Square (OLS) method is commonly used to estimate the unknown regression parameter.
+$$Y = X \times \beta + \epsilon, $$ where, $\beta$ is an p × 1 unknown regression paramaters and $\epsilon$ is the n × 1 vector of error with mean zero and equal variance.Ordinary Least Square (OLS) method is commonly used to estimate the unknown regression parameter.
 The OLS estimate in case of linear regression model is defined as follows,
@@
 
-One of the key assumption of the widely used multiple linear regression model is that the predictors need to be independent of each other. Violating the assumption of independence 
-results in an issue known as multicollinearity.
-Multicollinearity occurs when two or more independent variables are highly correlated with each other.
-It causes standard error of the OLS coefficient to increase resulting in wide confidence intervals and less reliable results.
-Identifying and interpreting significant predictors also becomes difficult.
-As the field of study progressed, researchers developed a number of methods to address presence of multicollinearity in data.
-Ridge regression [@hoerl1970ridge], Lasso,
+One of the key assumption of the widely used multiple linear regression model is that the predictors need to be independent of each other.
+Violating the assumption of independence results in an issue known as multicollinearity.
+Multicollinearity, originally identified by @frisch1934statistical, is the state in which two or more independent variables show a strong correlation with one another.
+It causes standard error of the OLS estimator to increase resulting in wide confidence intervals and less reliable results.
+Identifying and interpreting significant predictors also becomes difficult [@saleh2019theory].
+Increasing the sample size, eliminating the highly correlated variables, Principal component analysis are some of the ways to avoid multicollinearity but with the risk of losing either valuable information or interpretability.
+
+As the field of study progressed, researchers developed a number of methods to perform better than OLS in presence of multicollinearity in data by introducing bias to the estimator to gain smaller variance.
+Ridge regression [@hoerl1970ridge], Lasso [@tibshirani1996regression], Stein estimator [@stein1956inadmissibility], Modified ridge regression, Liu estimator [@liu1993new],
+Kibria-Lukman estimator [@kibria2020new] are some them.
 

### 2024-08-30 draft_1.qmd
updated introduction

@@
 
-As the field of study progressed, researchers developed a number of methods to perform better than OLS in presence of multicollinearity in data by introducing bias to the estimator to gain smaller variance.
-Ridge regression [@hoerl1970ridge], Lasso [@tibshirani1996regression], Stein estimator [@stein1956inadmissibility], Modified ridge regression, Liu estimator [@liu1993new],
-Kibria-Lukman estimator [@kibria2020new] are some them.
+As the field of study progressed, researchers developed a number of methods that outperforms OLS in presence of multicollinearity in data by introducing bias to the estimator to gain smaller variance.
+Ridge regression [@hoerl1970ridge], Lasso [@tibshirani1996regression], Stein estimator [@stein1956inadmissibility], Modified ridge regression, Liu estimator [@liu1993new], Kibria-Lukman estimator [@kibria2020new] are some of them.
+Among these, ridge regression has become one of the most popular methods for dealing with multicollinearity, providing a robust substitute for OLS.
+However, Ridge regression approach requires precise ridge parameter estimation, because the number of parameters, sample size, degree of correlation, and standard error vary greatly in real-world data.
+As a results numerous ridge parameters estimators has been suggested researchers till date.
+@mermi2024new in their recent paper presented and compared a total of 366 different ridge parameters estimators.
 
-Ridge regression is one of the methods proposed by @hoerl1970ridge that mitigates the effects of multicollinearity by introducing an amount of bias in to the model.
+Typically, the performance of various ridge settings are compared to OLS based on their mean square error (MSE).
+Nonetheless, certain unknown characteristics in the model determines when Ridge Regression estimators outperform Least Squares estimators in terms of MSE [@crivelli1995confidence].
+However, that does not tell us how well the corresponding ridge regression model performs in terms of finding out significance of the predictors which is one of the key points in regression analysis.
 
-para about differnt techniques,
+There are two ways by which statistical significance of the independent variables is determined.
+One is the method of hypothesis testing and the other one is the method of constructing Confidence Interval (CI).
+On the basis of power of the hypothesis test, a number of comparative studies have been done for ridge regression with various tuning settings [@halawa2000tests, @cule2011significance, @gokpinar2016study @perez2020some].
+Nevertheless, when evaluating regression parameters, confidence intervals are preferable to hypothesis testing because they offer a range of plausible values that represent the accuracy, direction and magnitude of the estimate.
+They provide a more precise grasp of practical significance based on sample size while avoiding the drawbacks of p-values [@nickerson2000null] .
+In practical fields such as, medical studies investigators are usually interested in determining the size of difference of a measured outcome between groups, rather than a simple indication of whether or not it is statistically significant [@gardner1986confidence].
+Therefore, CI's can be considered as more informative and transparent for making decisions.
 
-para about ridge
+This research examines the Confidence Intervals of multiple linear ridge regression settings for a number of shrinkage parameter under identical simulation conditions.
+The comparison is conducted based on the width of the confidence interval and coverage probability.
+The research might be useful to evaluate if shrinkage has produced more stable and dependable estimates than ordinary least squares (OLS) regression by evaluating the bias and variance reduction in Ridge Regression.
+We can also determine which tuning parameter gives a high coverage probability with a comparatively narrow indicating higher precision.
 
-para about CI
-
-para about Aim
-
-Note:
+The rest of the paper is organized as follows,
 

### 2024-09-09 draft_1.tex

@@
   pdftitle={Comparison of Confidence Interval in the OLS and Ridge Linear Regression Model: A Comparative study via Simulation},
-  pdfauthor={Sultana Mubarika Rahman Chowdhury; B.M Golam Kibria; Zoran Bursac},
+  pdfauthor={Sultana Mubarika Rahman Chowdhury; B.M. Golam Kibria; Zoran Bursac},
   pdfkeywords={Multiple Linear Regression, Ridge
@@
 Regression Model: A Comparative study via Simulation}
-\author{Sultana Mubarika Rahman Chowdhury$\textsuperscript{1}$, B.M
+\author{Sultana Mubarika Rahman Chowdhury$\textsuperscript{1}$, B.M.
 Golam Kibria$\textsuperscript{2}$, Zoran Bursac$\textsuperscript{1}$}
@@
 Violating the assumption of independence results in an issue known as
-multicollinearity. Multicollinearity occurs when two or more independent
-variables are highly correlated with each other. It causes standard
-error of the OLS coefficient to increase resulting in wide confidence
-intervals and less reliable results. Identifying and interpreting
-significant predictors also becomes difficult. As the field of study
-progressed, researchers developed a number of methods to address
-presence of multicollinearity in data. Ridge regression (Hoerl and
-Kennard 1970), Lasso,
+multicollinearity. Multicollinearity, originally identified by Frisch
+(1934), is the state in which two or more independent variables show a
+strong correlation with one another. It causes standard error of the OLS
+estimator to increase resulting in wide confidence intervals and less
+reliable results. Identifying and interpreting significant predictors
+also becomes difficult (Saleh, Arashi, and Kibria 2019). Increasing the
+sample size, eliminating the highly correlated variables, Principal
+component analysis are some of the ways to avoid multicollinearity but
+with the risk of losing either valuable information or interpretability.
 
-Ridge regression is one of the methods proposed by Hoerl and Kennard
-(1970) that mitigates the effects of multicollinearity by introducing an
-amount of bias in to the model.
+As the field of study progressed, researchers developed a number of
+methods that outperforms OLS in presence of multicollinearity in data by
+introducing bias to the estimator to gain smaller variance. Ridge
+regression (Hoerl and Kennard 1970), Lasso (Tibshirani 1996), Stein
+estimator (Stein et al. 1956), Modified ridge regression, Liu estimator
+(Liu 1993), Kibria-Lukman estimator (Kibria and Lukman 2020) are some of
+them. Among these, ridge regression has become one of the most popular
+methods for dealing with multicollinearity, providing a robust
+substitute for OLS. However, Ridge regression approach requires precise
+ridge parameter estimation, because the number of parameters, sample
+size, degree of correlation, and standard error vary greatly in
+real-world data. As a results numerous ridge parameters estimators has
+been suggested researchers till date. Mermi et al. (2024) in their
+recent paper presented and compared a total of 366 different ridge
+parameters estimators.
 
-para about differnt techniques,
+Typically, the performance of various ridge settings are compared to OLS
+based on their mean square error (MSE). Nonetheless, certain unknown
+characteristics in the model determines when Ridge Regression estimators
+outperform Least Squares estimators in terms of MSE (Crivelli et al.
+1995). However, that does not tell us how well the corresponding ridge
+regression model performs in terms of finding out significance of the
+predictors which is one of the key points in regression analysis.
 
-para about ridge
+There are two ways by which statistical significance of the independent
+variables is determined. One is the method of hypothesis testing and the
+other one is the method of constructing Confidence Interval (CI). On the
+basis of power of the hypothesis test, a number of comparative studies
+have been done for ridge regression with various tuning settings
+Perez-Melo and Kibria (2020). Nevertheless, when evaluating regression
+parameters, confidence intervals are preferable to hypothesis testing
+because they offer a range of plausible values that represent the
+accuracy, direction and magnitude of the estimate. They provide a more
+precise grasp of practical significance based on sample size while
+avoiding the drawbacks of p-values (Nickerson 2000) . In practical
+fields such as, medical studies investigators are usually interested in
+determining the size of difference of a measured outcome between groups,
+rather than a simple indication of whether or not it is statistically
+significant (Gardner and Altman 1986). Therefore, CI's can be considered
+as more informative and transparent for making decisions.
 
-para about CI
+This research examines the Confidence Intervals of multiple linear ridge
+regression settings for a number of shrinkage parameter under identical
+simulation conditions. The comparison is conducted based on the width of
+the confidence interval and coverage probability. The research might be
+useful to evaluate if shrinkage has produced more stable and dependable
+estimates than ordinary least squares (OLS) regression by evaluating the
+bias and variance reduction in Ridge Regression. We can also determine
+which tuning parameter gives a high coverage probability with a
+comparatively narrow indicating higher precision.
 
-para about Aim
-
-Note:
+The rest of the paper is organized as follows,
 
@@
 \begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-crivelli1995confidence}
+Crivelli, Ana, Luis Firinguetti, Rosa Montano, and Margarita Munóz.
+1995. {``Confidence Intervals in Ridge Regression by Bootstrapping the
+Dependent Variable: A Simulation Study.''} \emph{Communications in
+Statistics-Simulation and Computation} 24 (3): 631--52.
+
+\bibitem[\citeproctext]{ref-cule2011significance}
+Cule, Erika, Paolo Vineis, and Maria De Iorio. 2011. {``Significance
+Testing in Ridge Regression for Genetic Data.''} \emph{BMC
+Bioinformatics} 12: 1--15.
+
+\bibitem[\citeproctext]{ref-frisch1934statistical}
+Frisch, Ragnar. 1934. {``Statistical Confluence Analysis by Means of
+Complete Regression Systems.''} \emph{(No Title)}.
+
+\bibitem[\citeproctext]{ref-gardner1986confidence}
+Gardner, Martin J, and Douglas G Altman. 1986. {``Confidence Intervals
+Rather Than p Values: Estimation Rather Than Hypothesis Testing.''}
+\emph{Br Med J (Clin Res Ed)} 292 (6522): 746--50.
+
+\bibitem[\citeproctext]{ref-gokpinar2016study}
+Gökpınar, Esra, and Meral Ebegil. 2016. {``A Study on Tests of
+Hypothesis Based on Ridge Estimator.''} \emph{Gazi University Journal of
+Science} 29 (4): 769--81.
+
+\bibitem[\citeproctext]{ref-halawa2000tests}
+Halawa, AM, and MY El Bassiouni. 2000. {``Tests of Regression
+Coefficients Under Ridge Regression Models.''} \emph{Journal of
+Statistical Computation and Simulation} 65 (1-4): 341--56.
+
 \bibitem[\citeproctext]{ref-hoerl1970ridge}
@@
 
+\bibitem[\citeproctext]{ref-kibria2020new}
+Kibria, BM Golam, and Adewale F Lukman. 2020. {``A New Ridge-Type
+Estimator for the Linear Regression Model: Simulations and
+Applications.''} \emph{Scientifica} 2020 (1): 9758378.
+
+\bibitem[\citeproctext]{ref-liu1993new}
+Liu, Kejian. 1993. {``A New Class of Biased Estimate in Linear
+Regression.''} \emph{Communications in Statistics - Theory and Methods}
+22 (2): 393--402. \url{https://doi.org/10.1080/03610929308831027}.
+
+\bibitem[\citeproctext]{ref-mermi2024new}
+Mermi, Selman, Özge Akkuş, Atila Göktaş, and Necla Gündüz. 2024. {``A
+New Robust Ridge Parameter Estimator Having No Outlier and Ensuring
+Normality for Linear Regression Model.''} \emph{Journal of Radiation
+Research and Applied Sciences} 17 (1): 100788.
+
+\bibitem[\citeproctext]{ref-nickerson2000null}
+Nickerson, Raymond S. 2000. {``Null Hypothesis Significance Testing: A
+Review of an Old and Continuing Controversy.''} \emph{Psychological
+Methods} 5 (2): 241.
+
+\bibitem[\citeproctext]{ref-perez2020some}
+Perez-Melo, Sergio, and BM Golam Kibria. 2020. {``On Some Test
+Statistics for Testing the Regression Coefficients in Presence of
+Multicollinearity: A Simulation Study.''} \emph{Stats} 3 (1): 40--55.
+
+\bibitem[\citeproctext]{ref-saleh2019theory}
+Saleh, AK Md Ehsanes, Mohammad Arashi, and BM Golam Kibria. 2019.
+\emph{Theory of Ridge Regression Estimation with Applications}. John
+Wiley \& Sons.
+
+\bibitem[\citeproctext]{ref-stein1956inadmissibility}
+Stein, Charles et al. 1956. {``Inadmissibility of the Usual Estimator
+for the Mean of a Multivariate Normal Distribution.''} In
+\emph{Proceedings of the Third Berkeley Symposium on Mathematical
+Statistics and Probability}, 1:197--206. 1.
+
+\bibitem[\citeproctext]{ref-tibshirani1996regression}
+Tibshirani, Robert. 1996. {``Regression Shrinkage and Selection via the
+Lasso.''} \emph{Journal of the Royal Statistical Society Series B:
+Statistical Methodology} 58 (1): 267--88.
+
 \end{CSLReferences}

### 2024-09-11 draft_1.qmd
update introduction

@@
 The aim is to predict the response variable using the independent variables.
-If X is a n×p full rank matrix of predictors and Y is a n × 1 vector of response variables the multiple linear regression can be explained as,
-
-$$Y = X \times \beta + \epsilon, $$ where, $\beta$ is an p × 1 unknown regression paramaters and $\epsilon$ is the n × 1 vector of error with mean zero and equal variance.Ordinary Least Square (OLS) method is commonly used to estimate the unknown regression parameter.
-The OLS estimate in case of linear regression model is defined as follows,
-
-$$\hat{\beta} = (X^T X)^{-1} X^T y.$$
+If X is a n×p full rank matrix of predictors and Y is a n × 1 vector of response variables the multiple linear regression can be explained as, $$Y = X \beta + \epsilon,  $$ {#eq-test} where, $\beta$ is an p × 1 unknown regression paramaters and $\epsilon$ is the n × 1 vector of error with mean zero and equal variance.Ordinary Least Square (OLS) method is commonly used to estimate the unknown regression parameter.
+The OLS estimate in case of linear regression model is defined as follows, $$\hat{\beta} = (X^T X)^{-1} X^T y.$$ {#eq-1}
 
@@
 Increasing the sample size, eliminating the highly correlated variables, Principal component analysis are some of the ways to avoid multicollinearity but with the risk of losing either valuable information or interpretability.
-
 As the field of study progressed, researchers developed a number of methods that outperforms OLS in presence of multicollinearity in data by introducing bias to the estimator to gain smaller variance.
@@
 @mermi2024new in their recent paper presented and compared a total of 366 different ridge parameters estimators.
-
 Typically, the performance of various ridge settings are compared to OLS based on their mean square error (MSE).
 Nonetheless, certain unknown characteristics in the model determines when Ridge Regression estimators outperform Least Squares estimators in terms of MSE [@crivelli1995confidence].
-However, that does not tell us how well the corresponding ridge regression model performs in terms of finding out significance of the predictors which is one of the key points in regression analysis.
+However, that does not tell us how well the corresponding ridge regression model performs in terms of finding out significance of the predictors which is one of the key points in regression analysis.There are two ways by which statistical significance of the independent variables is determined.
+One is the method of hypothesis testing and the other one is the method of constructing Confidence Interval (CI).
 
-There are two ways by which statistical significance of the independent variables is determined.
-One is the method of hypothesis testing and the other one is the method of constructing Confidence Interval (CI).
 On the basis of power of the hypothesis test, a number of comparative studies have been done for ridge regression with various tuning settings [@halawa2000tests, @cule2011significance, @gokpinar2016study @perez2020some].
@@
 
+The inference for ridge regression based on confidence interval has not received much attention in the statistical literature.
+The earliest paper found was written by @obenchain1977classical.
+According to his results, ridge regression is a useful technique for handling multicollinear data without sacrificing the validity of statistical inference based on F and t tests, despite its bias [@obenchain1977classical].
+@vinod1987confidence studied four alternative methods to calculate confidence intervals ridge regression estimation.
+@crivelli1995confidence took into consideration two confidence intervals for the ridge regression parameters.The first is based on the standard normal distribution, while the second is based on the Edgeworth expansion of the standard normal distribution statistic, where the bootstrap concept is used to determine the percentile.
+A similar comparative study is done by @chaubey2018confidence where they compared confidence intervals constructed by Normal theory method, Percentile method, Studentized-t method, and Bias corrected accelerated method using Bootstarp and Jackknife methodology.
+@revan2023bootstrap in their most recent published work investigated confidence intervals constructed by standard normal approximation, student-t approximation and bootstrap method for different regularization parameters.
+Their finding indicate that both mean interval length and the coverage probability is affected by the choice of the shrinkage parameter.
+
 This research examines the Confidence Intervals of multiple linear ridge regression settings for a number of shrinkage parameter under identical simulation conditions.
@@
 
+--------\[ aim needs to be updated based on discussion\]
+
 The rest of the paper is organized as follows,
+
+------ \[write about different sections.\]
 
@@
 
-## Ridge Regression Estimators
+## Confidence Interval for OLS Estimators
 
-## Confidence Interval
+The OLS estimator $\hat{\beta}$ is an unbiased estimator of the ${\beta}$.
+Under the assumptions od the classical linear regression model the OLS estimator $\hat{\beta}$ is calculated by minimizing the sum of square of the residuals.
+To measure the variability of the estimate across samples the standard error is calculated as follows, $$ \text{SE}(\hat{\beta}) = \sqrt{\frac{\sigma^2}{\sum (x_i - \bar{x})^2}},
+$$ {#eq-2} where, $\sigma^2$ is the variance of the error term. Hence the confidence interval for $\hat{\beta}$ is given as, $$ \hat{\beta} \pm t_{\alpha/2, n-k} \cdot \text{SE}(\hat{\beta})
+$$ {#eq-3} where, $t_{\alpha/2, n-k}$ is the critical value for t- distribution with $n - k$ degrees of freedom for $n$ number of samples and $k$ predictors.
 
-## CI for Ridge regression
+## Confidence Interval for Ridge Regression Estimators
+
+The canonical form of model @eq-1 is written as, $$ y = Z\alpha + \epsilon, $$ {#eq-4} where, $Z = X Q$, $\alpha = Q^T \beta$ assuming $Q$ is a $p \times p$ orthogonal matrix, and $Z^T Z = \Lambda$ is a $p \times p$ diagonal matrix with eigen values ($\lambda_i$) as diagonal elements.
+The ridge regression estimator with k as the shrinkage parameter proposed by @hoerl1970ridge for $\alpha$ is written as, $$ \hat{\alpha} (k) = (Z^TZ + kI_p)^{-1} Z^Ty = W\hat{\alpha} $$ {#eq-5} where, $W = [I_p + k C^{-1}]^{-1}$ is the ridge regression estimator and $I_p$ is a identity matrix of order p.
+When there is multicollinearity among the regressors, $X^TX$ becomes singular or nearly singular, which means it cannot be inverted.
+Introducing a small positive number $kI_p$ to the diagonal elements making it always invertible thus it will always have a unique solution.
+
+## Ridge regression parameters
+
+CI for ridge,
+
+different k's
 

### 2024-09-12 draft_1.qmd

@@
 The canonical form of model @eq-1 is written as, $$ y = Z\alpha + \epsilon, $$ {#eq-4} where, $Z = X Q$, $\alpha = Q^T \beta$ assuming $Q$ is a $p \times p$ orthogonal matrix, and $Z^T Z = \Lambda$ is a $p \times p$ diagonal matrix with eigen values ($\lambda_i$) as diagonal elements.
-The ridge regression estimator with k as the shrinkage parameter proposed by @hoerl1970ridge for $\alpha$ is written as, $$ \hat{\alpha} (k) = (Z^TZ + kI_p)^{-1} Z^Ty = W\hat{\alpha} $$ {#eq-5} where, $W = [I_p + k C^{-1}]^{-1}$ is the ridge regression estimator and $I_p$ is a identity matrix of order p.
+The ridge regression estimator with k as the shrinkage parameter proposed by @hoerl1970ridge for $\alpha$ is written as, $$ \hat{\alpha} (k) = (Z^TZ + kI_p)^{-1} Z^Ty = W\hat{\alpha} ;     k \geq 0$$ {#eq-5} where, $W = [I_p + k C^{-1}]^{-1}$ is the ridge regression estimator, $k = diag(k_1, k_2,..., k_p)$ and $I_p$ is a identity matrix of order p.
 When there is multicollinearity among the regressors, $X^TX$ becomes singular or nearly singular, which means it cannot be inverted.
 Introducing a small positive number $kI_p$ to the diagonal elements making it always invertible thus it will always have a unique solution.
+The parameter k is known as the ridge parameter or shrinkage parameter.
 
-## Ridge regression parameters
+------- discuss whether to add different confidence interval
 
-CI for ridge,
+## Ridge Regression Parameters
 
-different k's
+In ridge regression the shrinkage parameter is estimated from the observed data.
+We must identify a ridge regression parameter that yields a less biased and consistent regression coefficient and has a smaller MSE value than the OLS estimator.
+Based on their performance in the MSE comparison with OLS, as reported in the literature, 18 distinct ridge regression parameters are chosen to be investigated in this research.
+This section gives the explanation and formulas of the parameters used in our simulation study.
+
+In the original paper @hoerl1970ridge suggested a parameter, $$\hat{k_i} = \frac{\hat{\sigma}^2}{\hat{\alpha_i}^2}$$ that minimizes the MSE of $\hat{\alpha}(k)$ defined by,
+
+$$\text{MSE}(\hat{\alpha}(k)) = \sigma^2 \sum_{i=1}^{p} \frac{\lambda_i}{(\lambda_i + \hat{k_i})^2} + \sum_{i=1}^{p} \frac{\hat{k_i}^2 \hat{\alpha_i}^2}{(\lambda_i + \hat{k_i})^2}$$ {#eq-7}
+
+here, $\hat{\sigma}^2 = \frac{\sum_{i=1}^{n} \hat{e}_i^2}{n - p}$
+
+The selected ridge parameters are listed below,
+
+@hocking1976class proposed k to be,
+$$k_1 = \frac{\hat\sigma^2_{} \sum(\hat\alpha_j^2 \lambda_j^2)}{(\sum(\hat\alpha_j^2 \lambda_j))^2}$$
+@hoerl1970ridge suggested k to be, $$ k_2 = \frac{\hat\sigma^2_{}}{\max(\hat\alpha^2)}$$
+@thisted1976ridge recommended k to be, $$k_3 = \frac{(p - 2) \hat{\sigma}^2_{}}{(\sum_{j=1}^{p} \hat{\beta}_{\text{j}})^2}$$
+@hoerl1976ridge suggested k to be, $$k_4 = \frac{p \hat{\sigma}^2_{}}{\sum_{j=1}^{p} (\hat{\alpha}^2_{\text{j}})}$$
+@kibria2003performance proposed k to be, $$k_5 = \text{median}\left(\frac{\hat{\sigma}^2_{}}{\hat{\alpha}^2{\text{j}}}\right)$$
+@khalaf2005choosing recommended k to be, $$k_6 = \frac{\lambda_{\text{max}} \hat{\sigma}^2_{}}{(n - p) \hat{\sigma}^2_{} + \hat{\lambda}_{\text{max}} \hat{\alpha}^2_{\text{max}}}$$
+@alkhamisi2006some  k to be, $k_7 = \max(m_j)$ and $k_8 = \text{median}(m_j)$ where, $$m_j = \frac{\lambda_{\text{j}} \hat{\sigma}^2_{}}{(n - p) \hat{\sigma}^2_{} + \lambda_{\text{j}} \hat{\alpha}^2_{\text{j}}}$$
+@schaffer1984higher suggested k to be, $$k_9 = \frac{1}{\hat{\alpha}^2_{\text{max}}}$$
+@asar2014modified advocated for the following k's $$k_{10} = \frac{p^2 \hat{\sigma}^2_{}}{\lambda^2_{\text{max}}\sum_{j=1}^{p} (\hat{\alpha}^2_{\text{j}})}$$
+$$k_{11} = \frac{p^3 \hat{\sigma}^2_{}}{\lambda^3_{\text{max}} \sum_{j=1}^{p} (\hat{\alpha}^2_{\text{j}})}$$
+$$k_{12} = \frac{p \hat{\sigma}^2_{}}{\lambda_{\text{max}}^{1/3} \sum_{j=1}^{p}(\hat{\alpha}^2_{\text{j}})}$$
+$$k_{13} = \frac{p^2 \hat{\sigma}^2_{}}{\left(\sum_{j=1}^{p} \sqrt{\lambda}\right)^{1/3} \sum_{j=1}^{p}(\hat{\alpha}^2_{\text{j}})}$$
+@nomura1988almost suggested \* check if correct $$k_{14} = \frac{p \hat{\sigma}^2_{}}{\sum_{j=1}^{p} \left( \frac{\hat{\alpha}^2_{\text{j}}}{1 + (1 + \lambda \sqrt{\frac{\hat{\alpha}^2_{\text{j}}}{\hat{\sigma}^2_{}}})} \right)}$$
+@dorugade2014new advocated for the following k's $$k_{15} = \text{median}\left(\frac{2 \hat{\sigma}^2_{}}{\lambda_{\text{max}} \hat{\alpha}^2_{\text{j}}}\right)$$
+$$k_{16} = \text{harmonic.mean}\left(\frac{2 \hat{\sigma}^2_{}}{\lambda_{\text{max}} \hat{\alpha}^2_{\text{j}}}\right)$$
+$$k_{17} = \text{geometric.mean}\left(\frac{2 \hat{\sigma}^2_{}}{\lambda_{\text{max}} \hat{\alpha}^2_{\text{j}}}\right)$$
+@batah2009ridge proposed the k to be, $$k_{18} = \frac{p \hat{\sigma}^2_{}}{\sum_{j=1}^{p} \left( \frac{\hat{\alpha}^2_{\text{j}}}{\sqrt{\frac{\hat{\alpha}^4_{\text{j}} \lambda^2_{\text{j}}}{4 \hat{\sigma}^4_{}} + \frac{6 \hat{\alpha}^2  \lambda_{\text{j}}}{\hat{\sigma}^2_{}}} - \frac{\hat{\alpha}^2_{\text{j}} \lambda_{\text{j}}}{2 \hat{\sigma}^2_{}}} \right)}$$ )
 

### 2024-09-16 draft_1.qmd
updated simulation section

@@
 
---------\[ aim needs to be updated based on discussion\]
-
 The rest of the paper is organized as follows,
@@
 The OLS estimator $\hat{\beta}$ is an unbiased estimator of the ${\beta}$.
-Under the assumptions od the classical linear regression model the OLS estimator $\hat{\beta}$ is calculated by minimizing the sum of square of the residuals.
+Under the assumptions of the classical linear regression model the OLS estimator $\hat{\beta}$ is calculated by minimizing the sum of square of the residuals.
 To measure the variability of the estimate across samples the standard error is calculated as follows, $$ \text{SE}(\hat{\beta}) = \sqrt{\frac{\sigma^2}{\sum (x_i - \bar{x})^2}},
@@
 
-------- discuss whether to add different confidence interval
+The standard error for Ridge regression is calculated after adjusting for the bias from the regularization parameter, The varinace-covariance matrix of the Ridge Regression estimator is,
+
+$$
+\text{Var}(\hat{\beta}_{\text{ridge}}) = \sigma^2 (Z^T Z + \lambda I)^{-1} Z^T Z (Z^T Z + \lambda I)^{-1}
+$$ Confidence interval for Ridge Regression is calculated using the Students-t approximation method where t-Statistics is,
+
+$$
+t_j = \frac{\hat{\beta}_{\text{ridge}, j}}{\hat{\text{SE}}(\hat{\beta}_{\text{ridge}, j})},
+$$ where, $\hat{\text{SE}}(\hat{\beta}_{\text{ridge}, j})$ is the standard error of the j-th coefficient. Hence, the j-th confidence interval is calculated using the following formula, $$
+\hat{\beta}_{\text{ridge}, j} \pm t_{\alpha/2, n-p} \cdot \hat{\text{SE}}(\hat{\beta}_{\text{ridge}, j}),
+$$ here, $t_{\alpha/2, n-p}$ is the critical value of the student's t-distribution with $n-p$ degrees of freedom.
 
@@
 
-@hocking1976class proposed k to be,
-$$k_1 = \frac{\hat\sigma^2_{} \sum(\hat\alpha_j^2 \lambda_j^2)}{(\sum(\hat\alpha_j^2 \lambda_j))^2}$$
-@hoerl1970ridge suggested k to be, $$ k_2 = \frac{\hat\sigma^2_{}}{\max(\hat\alpha^2)}$$
-@thisted1976ridge recommended k to be, $$k_3 = \frac{(p - 2) \hat{\sigma}^2_{}}{(\sum_{j=1}^{p} \hat{\beta}_{\text{j}})^2}$$
-@hoerl1976ridge suggested k to be, $$k_4 = \frac{p \hat{\sigma}^2_{}}{\sum_{j=1}^{p} (\hat{\alpha}^2_{\text{j}})}$$
-@kibria2003performance proposed k to be, $$k_5 = \text{median}\left(\frac{\hat{\sigma}^2_{}}{\hat{\alpha}^2{\text{j}}}\right)$$
-@khalaf2005choosing recommended k to be, $$k_6 = \frac{\lambda_{\text{max}} \hat{\sigma}^2_{}}{(n - p) \hat{\sigma}^2_{} + \hat{\lambda}_{\text{max}} \hat{\alpha}^2_{\text{max}}}$$
-@alkhamisi2006some  k to be, $k_7 = \max(m_j)$ and $k_8 = \text{median}(m_j)$ where, $$m_j = \frac{\lambda_{\text{j}} \hat{\sigma}^2_{}}{(n - p) \hat{\sigma}^2_{} + \lambda_{\text{j}} \hat{\alpha}^2_{\text{j}}}$$
-@schaffer1984higher suggested k to be, $$k_9 = \frac{1}{\hat{\alpha}^2_{\text{max}}}$$
-@asar2014modified advocated for the following k's $$k_{10} = \frac{p^2 \hat{\sigma}^2_{}}{\lambda^2_{\text{max}}\sum_{j=1}^{p} (\hat{\alpha}^2_{\text{j}})}$$
-$$k_{11} = \frac{p^3 \hat{\sigma}^2_{}}{\lambda^3_{\text{max}} \sum_{j=1}^{p} (\hat{\alpha}^2_{\text{j}})}$$
-$$k_{12} = \frac{p \hat{\sigma}^2_{}}{\lambda_{\text{max}}^{1/3} \sum_{j=1}^{p}(\hat{\alpha}^2_{\text{j}})}$$
-$$k_{13} = \frac{p^2 \hat{\sigma}^2_{}}{\left(\sum_{j=1}^{p} \sqrt{\lambda}\right)^{1/3} \sum_{j=1}^{p}(\hat{\alpha}^2_{\text{j}})}$$
-@nomura1988almost suggested \* check if correct $$k_{14} = \frac{p \hat{\sigma}^2_{}}{\sum_{j=1}^{p} \left( \frac{\hat{\alpha}^2_{\text{j}}}{1 + (1 + \lambda \sqrt{\frac{\hat{\alpha}^2_{\text{j}}}{\hat{\sigma}^2_{}}})} \right)}$$
-@dorugade2014new advocated for the following k's $$k_{15} = \text{median}\left(\frac{2 \hat{\sigma}^2_{}}{\lambda_{\text{max}} \hat{\alpha}^2_{\text{j}}}\right)$$
-$$k_{16} = \text{harmonic.mean}\left(\frac{2 \hat{\sigma}^2_{}}{\lambda_{\text{max}} \hat{\alpha}^2_{\text{j}}}\right)$$
-$$k_{17} = \text{geometric.mean}\left(\frac{2 \hat{\sigma}^2_{}}{\lambda_{\text{max}} \hat{\alpha}^2_{\text{j}}}\right)$$
-@batah2009ridge proposed the k to be, $$k_{18} = \frac{p \hat{\sigma}^2_{}}{\sum_{j=1}^{p} \left( \frac{\hat{\alpha}^2_{\text{j}}}{\sqrt{\frac{\hat{\alpha}^4_{\text{j}} \lambda^2_{\text{j}}}{4 \hat{\sigma}^4_{}} + \frac{6 \hat{\alpha}^2  \lambda_{\text{j}}}{\hat{\sigma}^2_{}}} - \frac{\hat{\alpha}^2_{\text{j}} \lambda_{\text{j}}}{2 \hat{\sigma}^2_{}}} \right)}$$ )
+@hocking1976class proposed k to be, $$k_1 = \frac{\hat\sigma^2_{} \sum(\hat\alpha_j^2 \lambda_j^2)}{(\sum(\hat\alpha_j^2 \lambda_j))^2}$$ @hoerl1970ridge suggested k to be, $$ k_2 = \frac{\hat\sigma^2_{}}{\max(\hat\alpha^2)}$$ @thisted1976ridge recommended k to be, $$k_3 = \frac{(p - 2) \hat{\sigma}^2_{}}{(\sum_{j=1}^{p} \hat{\beta}_{\text{j}})^2}$$ @hoerl1976ridge suggested k to be, $$k_4 = \frac{p \hat{\sigma}^2_{}}{\sum_{j=1}^{p} (\hat{\alpha}^2_{\text{j}})}$$ @kibria2003performance proposed k to be, $$k_5 = \text{median}\left(\frac{\hat{\sigma}^2_{}}{\hat{\alpha}^2{\text{j}}}\right)$$ @khalaf2005choosing recommended k to be, $$k_6 = \frac{\lambda_{\text{max}} \hat{\sigma}^2_{}}{(n - p) \hat{\sigma}^2_{} + \hat{\lambda}_{\text{max}} \hat{\alpha}^2_{\text{max}}}$$ @alkhamisi2006some k to be, $k_7 = \max(m_j)$ and $k_8 = \text{median}(m_j)$ where, $$m_j = \frac{\lambda_{\text{j}} \hat{\sigma}^2_{}}{(n - p) \hat{\sigma}^2_{} + \lambda_{\text{j}} \hat{\alpha}^2_{\text{j}}}$$ @schaffer1984higher suggested k to be, $$k_9 = \frac{1}{\hat{\alpha}^2_{\text{max}}}$$ @asar2014modified advocated for the following k's $$k_{10} = \frac{p^2 \hat{\sigma}^2_{}}{\lambda^2_{\text{max}}\sum_{j=1}^{p} (\hat{\alpha}^2_{\text{j}})}$$ $$k_{11} = \frac{p^3 \hat{\sigma}^2_{}}{\lambda^3_{\text{max}} \sum_{j=1}^{p} (\hat{\alpha}^2_{\text{j}})}$$ $$k_{12} = \frac{p \hat{\sigma}^2_{}}{\lambda_{\text{max}}^{1/3} \sum_{j=1}^{p}(\hat{\alpha}^2_{\text{j}})}$$ $$k_{13} = \frac{p^2 \hat{\sigma}^2_{}}{\left(\sum_{j=1}^{p} \sqrt{\lambda}\right)^{1/3} \sum_{j=1}^{p}(\hat{\alpha}^2_{\text{j}})}$$ @nomura1988almost suggested \* check if correct $$k_{14} = \frac{p \hat{\sigma}^2_{}}{\sum_{j=1}^{p} \left( \frac{\hat{\alpha}^2_{\text{j}}}{1 + (1 + \lambda \sqrt{\frac{\hat{\alpha}^2_{\text{j}}}{\hat{\sigma}^2_{}}})} \right)}$$ @dorugade2014new advocated for the following k's $$k_{15} = \text{median}\left(\frac{2 \hat{\sigma}^2_{}}{\lambda_{\text{max}} \hat{\alpha}^2_{\text{j}}}\right)$$ $$k_{16} = \text{harmonic.mean}\left(\frac{2 \hat{\sigma}^2_{}}{\lambda_{\text{max}} \hat{\alpha}^2_{\text{j}}}\right)$$ $$k_{17} = \text{geometric.mean}\left(\frac{2 \hat{\sigma}^2_{}}{\lambda_{\text{max}} \hat{\alpha}^2_{\text{j}}}\right)$$ @batah2009ridge proposed the k to be, $$k_{18} = \frac{p \hat{\sigma}^2_{}}{\sum_{j=1}^{p} \left( \frac{\hat{\alpha}^2_{\text{j}}}{\sqrt{\frac{\hat{\alpha}^4_{\text{j}} \lambda^2_{\text{j}}}{4 \hat{\sigma}^4_{}} + \frac{6 \hat{\alpha}^2  \lambda_{\text{j}}}{\hat{\sigma}^2_{}}} - \frac{\hat{\alpha}^2_{\text{j}} \lambda_{\text{j}}}{2 \hat{\sigma}^2_{}}} \right)}$$ )
 
-# Simulation Study
+# Simulation Design
+
+The process of Monte Carlo simulation is used for the simulation study in order to evaluate the performance of the shrinkage parameters. The steps of the procedures is given as follows,
+
+1) The independent variables are generated by following the method of @mcdonald1975monte as follows,
+
+$$
+x_{ij} = \left(1 - \rho^2 \right)^{1/2} w_{ij} + \rho w_{i(p+1)}, \quad j = 1, \dots, p, \quad i = 1, \dots, n
+$$
+here, $w_{ij}$ is the error term $\rho$ is the correlation between two predictors, p is the number of explanatory variables and, n is the number of samples.
+The number of sample considered for the study are, $n = 30, 100$ and level of collinearity taken are, $\rho = 0.80, 0.85, 0.90, 0.95, 0.99$.
+
+2) Therefore the observations are derive using the following regression model, 
+$$
+y_i = \beta_1 x_{i1} + \dots + \beta_p x_{ip} + \epsilon_i, \quad i = 1, \dots, n
+$$
+3) The error term are generated from pseudo-random independent standard normal numbers with mean zero and unit variance.
+
+*** needs to be edited
+
+4) values of s
+
+5) number of iteration
+
+6) calculating of confidence interval
+
+7) calculation of coverage probability
+
+   software used **** needs to be edited
 

### 2024-09-30 draft_1.qmd
added parameter
update

--- 2024-09-11 draft_1.qmd
@@
 title: "Comparison of Confidence Interval in the OLS and Ridge Linear Regression Model: A Comparative study via Simulation"
-format: #docx
-    tandf-pdf:
-      keep-tex: true  
-    tandf-html: default
+format: docx
+    # tandf-pdf:
+    #   keep-tex: true  
+    # tandf-html: default
 author:
@@
 The aim is to predict the response variable using the independent variables.
-If X is a n×p full rank matrix of predictors and Y is a n × 1 vector of response variables the multiple linear regression can be explained as, $$Y = X \beta + \epsilon,  $$ {#eq-test} where, $\beta$ is an p × 1 unknown regression paramaters and $\epsilon$ is the n × 1 vector of error with mean zero and equal variance.Ordinary Least Square (OLS) method is commonly used to estimate the unknown regression parameter.
-The OLS estimate in case of linear regression model is defined as follows, $$\hat{\beta} = (X^T X)^{-1} X^T y.$$ {#eq-1}
-
+Ordinary Least Square (OLS) method is commonly used to estimate the unknown regression parameter.
 One of the key assumption of the widely used multiple linear regression model is that the predictors need to be independent of each other.
@@
 Among these, ridge regression has become one of the most popular methods for dealing with multicollinearity, providing a robust substitute for OLS.
+
 However, Ridge regression approach requires precise ridge parameter estimation, because the number of parameters, sample size, degree of correlation, and standard error vary greatly in real-world data.
@@
 On the basis of power of the hypothesis test, a number of comparative studies have been done for ridge regression with various tuning settings [@halawa2000tests, @cule2011significance, @gokpinar2016study @perez2020some].
-Nevertheless, when evaluating regression parameters, confidence intervals are preferable to hypothesis testing because they offer a range of plausible values that represent the accuracy, direction and magnitude of the estimate.
+Nevertheless, when evaluating regression parameters, CIs are preferable to hypothesis testing because they offer a range of plausible values that represent the accuracy, direction and magnitude of the estimate.
 They provide a more precise grasp of practical significance based on sample size while avoiding the drawbacks of p-values [@nickerson2000null] .
@@
 
-The inference for ridge regression based on confidence interval has not received much attention in the statistical literature.
+The inference for ridge regression based on CI has not received much attention in the statistical literature.
 The earliest paper found was written by @obenchain1977classical.
 According to his results, ridge regression is a useful technique for handling multicollinear data without sacrificing the validity of statistical inference based on F and t tests, despite its bias [@obenchain1977classical].
-@vinod1987confidence studied four alternative methods to calculate confidence intervals ridge regression estimation.
-@crivelli1995confidence took into consideration two confidence intervals for the ridge regression parameters.The first is based on the standard normal distribution, while the second is based on the Edgeworth expansion of the standard normal distribution statistic, where the bootstrap concept is used to determine the percentile.
-A similar comparative study is done by @chaubey2018confidence where they compared confidence intervals constructed by Normal theory method, Percentile method, Studentized-t method, and Bias corrected accelerated method using Bootstarp and Jackknife methodology.
-@revan2023bootstrap in their most recent published work investigated confidence intervals constructed by standard normal approximation, student-t approximation and bootstrap method for different regularization parameters.
+@vinod1987confidence studied four alternative methods to calculate CIs ridge regression estimation.
+@crivelli1995confidence took into consideration two CIs for the ridge regression parameters.The first is based on the standard normal distribution, while the second is based on the Edgeworth expansion of the standard normal distribution statistic, where the bootstrap concept is used to determine the percentile.
+A similar comparative study is done by @chaubey2018confidence where they compared CIs constructed by Normal theory method, Percentile method, Studentized-t method, and Bias corrected accelerated method using Bootstarp and Jackknife methodology.
+@revan2023bootstrap in their most recent published work investigated CIs constructed by standard normal approximation, student-t approximation and bootstrap method for different regularization parameters.
 Their finding indicate that both mean interval length and the coverage probability is affected by the choice of the shrinkage parameter.
 
-This research examines the Confidence Intervals of multiple linear ridge regression settings for a number of shrinkage parameter under identical simulation conditions.
-The comparison is conducted based on the width of the confidence interval and coverage probability.
+This research examines the CIs of multiple linear ridge regression settings for a number of shrinkage parameter under identical simulation conditions.
+The comparison is conducted based on the width of the CI and coverage probability.
 The research might be useful to evaluate if shrinkage has produced more stable and dependable estimates than ordinary least squares (OLS) regression by evaluating the bias and variance reduction in Ridge Regression.
 We can also determine which tuning parameter gives a high coverage probability with a comparatively narrow indicating higher precision.
-
---------\[ aim needs to be updated based on discussion\]
 
@@
 
-## Confidence Interval for OLS Estimators
+## Confidence Interval for OLS and Ridge Regression Estimators
 
-The OLS estimator $\hat{\beta}$ is an unbiased estimator of the ${\beta}$.
-Under the assumptions od the classical linear regression model the OLS estimator $\hat{\beta}$ is calculated by minimizing the sum of square of the residuals.
+If X is a n×p full rank matrix of predictors and Y is a n × 1 vector of response variables the multiple linear regression can be explained as, $$Y = X \beta + \epsilon,  $$ {#eq-1}
+
+where, $\beta$ is an p × 1 unknown regression parameters and $\epsilon$ is the n × 1 vector of error with mean zero and equal variance.
+The OLS estimate ($\hat{\beta}$) is an unbiased estimator of the ${\beta}$.
+In case of linear regression model is defined as follows, $$\hat{\beta} = (X^{'} X)^{-1} X^{'} y.$$ {#eq-2}
+
+Under the assumptions of the classical linear regression model the OLS estimator $\hat{\beta}$ is calculated by minimizing the sum of square of the residuals.
 To measure the variability of the estimate across samples the standard error is calculated as follows, $$ \text{SE}(\hat{\beta}) = \sqrt{\frac{\sigma^2}{\sum (x_i - \bar{x})^2}},
-$$ {#eq-2} where, $\sigma^2$ is the variance of the error term. Hence the confidence interval for $\hat{\beta}$ is given as, $$ \hat{\beta} \pm t_{\alpha/2, n-k} \cdot \text{SE}(\hat{\beta})
-$$ {#eq-3} where, $t_{\alpha/2, n-k}$ is the critical value for t- distribution with $n - k$ degrees of freedom for $n$ number of samples and $k$ predictors.
+$$ {#eq-3} where, $\sigma^2$ is the variance of the error term. Hence, the confidence interval for $\hat{\beta}$ is given as, $$ \hat{\beta} \pm t_{\alpha/2, n-k} \cdot \text{SE}(\hat{\beta})
+$$ {#eq-4} where, $t_{\alpha/2, n-k}$ is the critical value for t- distribution with $n - k$ degrees of freedom for $n$ number of samples and $k$ predictors.
 
-## Confidence Interval for Ridge Regression Estimators
+The ridge regression estimator proposed by @hoerl1970ridge introduces a small amount of bias to reduce the standard errors. The estimator is given by,
 
-The canonical form of model @eq-1 is written as, $$ y = Z\alpha + \epsilon, $$ {#eq-4} where, $Z = X Q$, $\alpha = Q^T \beta$ assuming $Q$ is a $p \times p$ orthogonal matrix, and $Z^T Z = \Lambda$ is a $p \times p$ diagonal matrix with eigen values ($\lambda_i$) as diagonal elements.
-The ridge regression estimator with k as the shrinkage parameter proposed by @hoerl1970ridge for $\alpha$ is written as, $$ \hat{\alpha} (k) = (Z^TZ + kI_p)^{-1} Z^Ty = W\hat{\alpha} $$ {#eq-5} where, $W = [I_p + k C^{-1}]^{-1}$ is the ridge regression estimator and $I_p$ is a identity matrix of order p.
-When there is multicollinearity among the regressors, $X^TX$ becomes singular or nearly singular, which means it cannot be inverted.
+$$ \hat\beta_{ridge} = (X^{'}X +kI_p)^{-1}X^{'}y: k>0 $$ {#eq-5}
+
+When there is multicollinearity among the regressors, $X^{'}X$ becomes singular or nearly singular, which means it cannot be inverted.
 Introducing a small positive number $kI_p$ to the diagonal elements making it always invertible thus it will always have a unique solution.
+The parameter k is known as the ridge parameter or shrinkage parameter.
+
+The standard error for ridge regression is calculated after adjusting for the bias from the regularization parameter, The variance-covariance matrix of the Ridge Regression estimator is,
+
+$$
+\text{Var}(\hat{\beta}_{\text{ridge}}) = \sigma^2 (Z^T Z + \lambda I)^{-1} Z^T Z (Z^T Z + \lambda I)^{-1}
+$$ {#eq-6}
+
+Confidence interval for ridge regression is calculated using the Students-t approximation method where t-statistics is,
+
+$$
+t_j = \frac{\hat{\beta}_{\text{ridge}, j}}{\hat{\text{SE}}(\hat{\beta}_{\text{ridge}, j})},
+$$ {#eq-7}
+
+where, $\hat{\text{SE}}(\hat{\beta}_{\text{ridge}, j})$ is the standard error of the j-th coefficient. Hence, the j-th confidence interval is calculated using the following formula, $$
+\hat{\beta}_{\text{ridge}, j} \pm t_{\alpha/2, n-p} \cdot \hat{\text{SE}}(\hat{\beta}_{\text{ridge}, j}),
+$$ {#eq-8} here, $t_{\alpha/2, n-p}$ is the critical value of the student's t-distribution with $n-p$ degrees of freedom.
 
@@
 
-CI for ridge,
+In ridge regression the shrinkage parameter is estimated from the observed data.
+We must identify a ridge regression parameter that yields a less biased and consistent regression coefficient and has a smaller MSE value than the OLS estimator.
+Based on their performance in the MSE comparison with OLS, as reported in the literature, 18 distinct ridge regression parameters are chosen to be investigated in this research.
+This section gives the explanation and formulas of the parameters used in our simulation study.
 
-different k's
+In the original paper @hoerl1970ridge suggested a parameter, $$\hat{k_i} = \frac{\hat{\sigma}^2}{\hat{\alpha_i}^2}$$ that minimizes the MSE of $\hat{\alpha}(k)$ defined by,
 
-# Simulation Study
+$$
+\text{MSE}(\hat{\alpha}(k)) = \sigma^2 \sum_{i=1}^{p} \frac{\lambda_i}{(\lambda_i + \hat{k_i})^2} + \sum_{i=1}^{p} \frac{\hat{k_i}^2 \hat{\alpha_i}^2}{(\lambda_i + \hat{k_i})^2}
+$$
+
+here, $\hat{\sigma}^2 = \frac{\sum_{i=1}^{n} \hat{e}_i^2}{n - p}$
+
+The selected ridge parameters are listed below,
+
+@hocking1976class proposed k to be,\
+$$
+k_1 = \frac{\hat\sigma^2_{} \sum(\hat\alpha_j^2 \lambda_j^2)}{(\sum(\hat\alpha_j^2 \lambda_j))^2}
+$$ @hoerl1970ridge suggested k to be, $$ 
+k_2 = \frac{\hat\sigma^2_{}}{\max(\hat\alpha^2)}
+$$ @thisted1976ridge recommended k to be,$$
+k_3 = \frac{(p - 2) \hat{\sigma}^2_{}}{(\sum_{j=1}^{p} \hat{\beta}_{\text{j}})^2}
+$$ @hoerl1976ridge suggested k to be, $$
+k_4 = \frac{p \hat{\sigma}^2_{}}{\sum_{j=1}^{p} (\hat{\alpha}^2_{\text{j}})}
+$$ @kibria2003performance proposed k to be, $$
+k_5 = \text{median}\left(\frac{\hat{\sigma}^2_{}}{\hat{\alpha}^2{\text{j}}}\right)
+$$ @khalaf2005choosing recommended k to be, $$
+k_6 = \frac{\lambda_{\text{max}} \hat{\sigma}^2_{}}{(n - p) \hat{\sigma}^2_{} + \hat{\lambda}_{\text{max}} \hat{\alpha}^2_{\text{max}}}
+$$ @alkhamisi2006some k to be, $k_7 = \max(m_j)$ and $k_8 = \text{median}(m_j)$ where, $$
+m_j = \frac{\lambda_{\text{j}} \hat{\sigma}^2_{}}{(n - p) \hat{\sigma}^2_{} + \lambda_{\text{j}} \hat{\alpha}^2_{\text{j}}}
+$$ @schaffer1984higher suggested k to be, $$
+k_9 = \frac{1}{\hat{\alpha}^2_{\text{max}}}
+$$ @asar2014modified advocated for the following k's $$
+k_{10} = \frac{p^2 \hat{\sigma}^2_{}}{\lambda^2_{\text{max}}\sum_{j=1}^{p} (\hat{\alpha}^2_{\text{j}})}
+$$ $$
+k_{11} = \frac{p^3 \hat{\sigma}^2_{}}{\lambda^3_{\text{max}} \sum_{j=1}^{p} (\hat{\alpha}^2_{\text{j}})}
+$$ $$
+k_{12} = \frac{p \hat{\sigma}^2_{}}{\lambda_{\text{max}}^{1/3} \sum_{j=1}^{p}(\hat{\alpha}^2_{\text{j}})}
+$$ $$
+k_{13} = \frac{p^2 \hat{\sigma}^2_{}}{\left(\sum_{j=1}^{p} \sqrt{\lambda}\right)^{1/3} \sum_{j=1}^{p}(\hat{\alpha}^2_{\text{j}})}
+$$ @nomura1988almost suggested \* check if correct
+
+$$
+k_{14} = \frac{p \hat{\sigma}^2_{}}{\sum_{j=1}^{p} \left( \frac{\hat{\alpha}^2_{\text{j}}}{1 + (1 + \lambda \sqrt{\frac{\hat{\alpha}^2_{\text{j}}}{\hat{\sigma}^2_{}}})} \right)}
+$$ @dorugade2014new advocated for the following k's $$
+k_{15} = \text{median}\left(\frac{2 \hat{\sigma}^2_{}}{\lambda_{\text{max}} \hat{\alpha}^2_{\text{j}}}\right)
+$$ $$
+k_{16} = \text{harmonic.mean}\left(\frac{2 \hat{\sigma}^2_{}}{\lambda_{\text{max}} \hat{\alpha}^2_{\text{j}}}\right)
+$$ $$
+k_{17} = \text{geometric.mean}\left(\frac{2 \hat{\sigma}^2_{}}{\lambda_{\text{max}} \hat{\alpha}^2_{\text{j}}}\right)
+$$ @chandnew proposed the following k's, $$
+\hat{k}_{18} = \hat{\sigma} p \left(1 + \frac{p}{n} \right)
+$$,
+
+$$
+\hat{k}_{19} = \hat{\sigma} \times \max \left( p ^\left(1 + \frac{p}{n} \right), p^{\left(1 + \frac{1}{p}\right)} \right)
+$$
+
+# Simulation Design
+
+The process of Monte Carlo simulation is used for the designsimulation study in order to evaluate the performance of the shrinkage parameters. The steps of the procedures is given as follows,
+
+1)  The independent variables are generated by following the method of @mcdonald1975monte as follows,
+
+$$
+x_{ij} = \left(1 - \rho^2 \right)^{1/2} w_{ij} + \rho w_{i(p+1)}, \quad j = 1, \dots, p, \quad i = 1, \dots, n
+$$ here, $w_{ij}$ is the error term $\rho$ is the correlation between two predictors, p is the number of explanatory variables and, n is the number of samples.
+Eigen values $(\lambda_1, \lambda_2, ...
+\lambda_p)$ and corresponding eigen vectors of matrix $X^{'}X$ are computed.
+
+3)  The error term $\epsilon_i$ are generated from pseudo-random independent standard normal numbers with mean zero and $\sigma^2$ variance.
+
+4)  The final observations were derived by using the following equation,
+
+$$y_i = \beta_0 + \beta_1 x_{i1} + \dots + \beta_p x_{ip} + \epsilon_i, \quad i = 1, \dots, n
+$$ here without loss of generality the intercept is assumed to be zero in @eq-7. The values of $\beta$ are chosen in a way that $\beta^{'}\beta = 1$
+
+6)  The selected 19 shrinkage parameters are then calculated using the formulas in the previous section.
+
+7)  For each one of the 19 shrinkage parameters OLS estimator and ridge regression estimator is then calculated along with the 95% confidence interval width using equations @eq-2, @eq-4, @eq-5, @eq-8.
+
+8)  The simulation process is iterated 5000 times for each model specification of sample size , $n$ = 30, 50, 100, level of collinearity , $\rho$ = 0.60, 0.80, 0.85, 0.90, 0.95, 0.99 and $\sigma^2$ = 1, 3, 5, 10.
+
+9)  Estimated mean square error for each of the 19 k-parameters is calculated by taking an average of 5000 simulation using the following formula, $$
+    MSE(\hat{\beta}) = \frac{1}{5000} \sum_{i=1}^{5000} (\hat{\beta_i} - \beta_i)' (\hat{\beta_i} - \beta_i),
+    $$
+
+10) The average confidence interval(CI) width and coverage probability(CP) for each shrinkage parameter are calculated by the formula as follows,
+
+$$
+CI width = \frac{\sum_{i=1}^{5000} (\hat{\beta}_U - \hat{\beta}_L)}{5000},
+$$
+$$
+CP = \frac{\#(\hat{\beta}_L < \beta < \hat{\beta}_U)}{5000},
+$$
+All computations are performed with the R Statistical Software (v4.4.0; @r_soft).
+
+***** explain something about the tables
+
+# Results
 
@@
 
+Extra:
+
+The canonical form of model @eq-1 is written as, $$ y = Z\alpha + \epsilon, $$ where, $Z = X Q$, $\alpha = (\alpha_1, \alpha_2, ..., \alpha_p) = Q^T \beta$ assuming $Q$ is a $p \times p$ orthogonal matrix such that $Q^{'}Q = I_p$, and $Q^{'}X^{'}XQ = \Lambda$, where $\Lambda =diag(\lambda_1, \lambda_2, ..., \lambda_p)$ is the orthogonal matrix that consists of the eigen values of $X^{'}X$.
+
+Then the OLS estimator is canonical form is given below,
+
+$$ \hat\alpha_{OLS} = (Z^{'}Z)^{-1}Z{'}y $$
+
+The ridge regression estimator with k as the shrinkage parameter proposed by @hoerl1970ridge for $\alpha$ is written as, $$ \hat{\alpha} (k) = (Z^TZ + kI_p)^{-1} Z^Ty = W\hat{\alpha} ;     k \geq 0$$ where, $W = [I_p + k C^{-1}]^{-1}$ is the ridge regression estimator, $k = diag(k_1, k_2,..., k_p)$ and $I_p$ is a identity matrix of order p.
+
 # Bibliography

### 2024-10-01 plots.qmd
codes for plot 1

---
title: "plots"
format: html
editor: visual
---
# Plot 1

```{r}

# Load necessary libraries
if (!require(ggplot2)) install.packages("ggplot2")
if (!require(gridExtra)) install.packages("gridExtra")
if (!require(reshape2)) install.packages("reshape2")
if (!require(gtable)) install.packages("gtable")  # Required for gtable_filter
if (!require(grid)) install.packages("grid")

library(ggplot2)
library(gridExtra)
library(reshape2)
library(gtable)
library(grid)

# Create the data frame based on Table 1 (MSE values)
data <- data.frame(
  rho = c(0.60, 0.80, 0.85, 0.90, 0.95, 0.99),
  OLS = c(0.19, 0.359, 0.479, 0.73, 1.521, 9.75),
  k1 = c(0.214, 0.412, 0.518, 0.675, 0.941, 8.486),
  k2 = c(0.207, 0.376, 0.474, 0.648, 0.875, 38.301),
  k3 = c(0.283, 0.494, 0.58, 0.687, 0.825, 1.543),
  k4 = c(0.237, 0.401, 0.483, 0.612, 0.904, 21.909),
  k5 = c(0.598, 0.697, 0.734, 0.79, 0.909, 9.19),
  k6 = c(0.202, 0.38, 0.494, 0.708, 1.329, 72.98),
  k7 = c(0.174, 0.314, 0.396, 0.524, 0.737, 1.877),
  k8 = c(0.176, 0.324, 0.428, 0.642, 1.309, 62.724),
  k9 = c(0.207, 0.375, 0.473, 0.648, 1.107, 67.02),
  k10 = c(0.19, 0.359, 0.479, 0.73, 1.52, 75.52),
  k11 = c(0.19, 0.359, 0.479, 0.73, 1.521, 75.668),
  k12 = c(0.192, 0.361, 0.481, 0.714, 1.439, 67.185),
  k13 = c(0.216, 0.383, 0.473, 0.618, 0.946, 22.87),
  k14 = c(0.6, 0.64, 0.658, 0.689, 0.77, 8.675),
  k15 = c(0.218, 0.363, 0.458, 0.644, 1.187, 48.062),
  k16 = c(0.191, 0.36, 0.478, 0.719, 1.464, 69.634),
  k17 = c(0.2, 0.35, 0.447, 0.63, 1.134, 37.093),
  k18 = c(0.191, 0.34, 0.423, 0.552, 0.758, 1.285),
  k19 = c(0.191, 0.34, 0.423, 0.552, 0.758, 1.285)
)

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = 'rho', variable.name = 'Estimator', value.name = 'MSE')

# Create the grouped bar plot
mse_plot_n30_p3 <-ggplot(data_long, aes(x = Estimator, y = MSE, fill = factor(rho))) +
  geom_bar(stat = "identity", position = "dodge") +  # Group bars by rho
  scale_fill_brewer(palette = "Set3") +  # Use a distinct color palette
  labs(title = "MSE (n = 30, p = 3)",
       x = "Estimator", y = "Mean Squared Error (MSE)", fill = expression(rho)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),  
        axis.title = element_text(size = 10),
        plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))

# plot for coverage probability n = 30, p = 3 , s = 1

# Create the data frame based on Table 2 (Coverage Probability values)
data <- data.frame(
  rho = c(0.60, 0.80, 0.85, 0.90, 0.95, 0.99),
  OLS = c(0.953, 0.958, 0.957, 0.956, 0.953, 0.953),
  k1 = c(0.867, 0.686, 0.591, 0.472, 0.333, 0.179),
  k2 = c(0.887, 0.793, 0.752, 0.697, 0.639, 0.711),
  k3 = c(0.733, 0.454, 0.436, 0.25, 0.133, 0.024),
  k4 = c(0.788, 0.649, 0.603, 0.546, 0.483, 0.489),
  k5 = c(0.202, 0.174, 0.177, 0.181, 0.197, 0.197),
  k6 = c(0.916, 0.852, 0.814, 0.75, 0.676, 0.797),
  k7 = c(0.916, 0.817, 0.744, 0.619, 0.336, 0.003),
  k8 = c(0.953, 0.954, 0.955, 0.955, 0.954, 0.953),
  k9 = c(0.886, 0.796, 0.754, 0.699, 0.642, 0.711),
  k10 = c(0.953, 0.957, 0.956, 0.955, 0.953, 0.953),
  k11 = c(0.953, 0.957, 0.956, 0.956, 0.953, 0.953),
  k12 = c(0.945, 0.928, 0.914, 0.9, 0.527, 0.9),
  k13 = c(0.854, 0.726, 0.674, 0.611, 0.502, 0.611),
  k14 = c(0.05, 0.092, 0.121, 0.164, 0.227, 0.215),
  k15 = c(0.871, 0.847, 0.832, 0.81, 0.794, 0.933),
  k16 = c(0.947, 0.935, 0.926, 0.915, 0.941, 0.944),
  k17 = c(0.91, 0.875, 0.857, 0.826, 0.811, 0.737),
  k18 = c(0.879, 0.736, 0.65, 0.479, 0.174, 0.737),
  k19 = c(0.879, 0.736, 0.65, 0.479, 0.174, 0.737)
)

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = 'rho', variable.name = 'Estimator', value.name = 'CoverageProbability')

# Create the line plot for coverage probability
coverage_prob_plot_n30_p3 <- ggplot(data_long, aes(x = rho, y = CoverageProbability, color = Estimator)) +
  geom_point(size = 3) +                            # Add points
  geom_line(aes(group = Estimator), linetype = "dashed", size = 0.8) +  # Add dashed lines
  labs(title = "Coverage Probability (n = 30, p = 3)",
       x = expression(rho), y = "Coverage Probability") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8),  
        axis.title = element_text(size = 10),
        plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))

# plot for CI width n = 30, p = 3 , s = 1

# Create the data frame based on the provided table (Table 3)
data <- data.frame(
  rho = c(0.60, 0.80, 0.85, 0.90, 0.95, 0.99),
  OLS = c(0.923, 1.365, 1.627, 2.089, 3.189, 8.121),
  k1 = c(0.806, 0.912, 0.926, 0.922, 0.895, 0.878),
  k2 = c(0.823, 1.042, 1.145, 1.308, 1.675, 3.451),
  k3 = c(0.677, 0.641, 0.608, 0.551, 0.454, 0.309),
  k4 = c(0.724, 0.838, 0.889, 0.931, 1.163, 7.252),
  k5 = c(0.39, 0.427, 0.451, 0.492, 0.592, 0.935),
  k6 = c(0.861, 1.147, 1.29, 1.515, 2.035, 3.483),
  k7 = c(0.782, 0.906, 0.94, 0.956, 0.586, 2.331),
  k8 = c(0.88, 1.275, 1.158, 1.923, 2.902, 2.633),
  k9 = c(0.827, 1.052, 1.158, 1.923, 2.699, 2.635),
  k10 = c(0.923, 1.364, 1.535, 2.084, 3.175, 8.052),
  k11 = c(0.923, 1.364, 1.535, 2.084, 3.175, 8.052),
  k12 = c(0.907, 1.302, 1.522, 1.893, 2.737, 6.459),
  k13 = c(0.782, 0.936, 0.998, 1.088, 1.283, 2.271),
  k14 = c(0.37, 0.413, 0.437, 0.48, 0.591, 1.196),
  k15 = c(0.807, 1.115, 1.29, 1.572, 2.208, 4.949),
  k16 = c(0.912, 1.132, 1.517, 1.943, 2.845, 6.623),
  k17 = c(0.839, 1.15, 1.317, 1.754, 2.175, 4.013),
  k18 = c(0.732, 0.833, 0.855, 0.854, 0.771, 0.485),
  k19 = c(0.732, 0.833, 0.855, 0.854, 0.771, 0.485)
)

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = 'rho', variable.name = 'Estimator', value.name = 'CI_Width')

# Create the grouped bar plot
ci_width_plot_n30_p3 <- ggplot(data_long, aes(x = Estimator, y = CI_Width, fill = factor(rho))) +
  geom_bar(stat = "identity", position = "dodge") +  # Group bars by rho
  scale_fill_brewer(palette = "Set3") +  # Use a distinct color palette
  labs(title = "Confidence Interval Width (n = 30, p = 3)",
       x = "Estimator", y = "Confidence Interval Width", fill = expression(rho)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),   axis.title = element_text(size = 10),
  plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))

# Plot for MSE for n = 100, p = 3 , s = 1

# Create the data frame based on Table 15 (MSE values)
data <- data.frame(
  rho = c(0.60, 0.80, 0.85, 0.90, 0.95, 0.99),
  OLS = c(0.431, 0.643, 0.768, 0.987, 1.508, 3.841),
  k1 = c(0.42, 0.584, 0.649, 0.701, 0.673, 1.19),
  k2 = c(0.421, 0.604, 0.701, 0.845, 1.09, 4.87),
  k3 = c(0.404, 0.476, 0.475, 0.445, 0.335, 0.403),
  k4 = c(0.404, 0.549, 0.616, 0.704, 0.831, 3.062),
  k5 = c(0.195, 0.224, 0.245, 0.281, 0.356, 1.617),
  k6 = c(0.424, 0.614, 0.718, 0.885, 1.206, 8.694),
  k7 = c(0.409, 0.557, 0.627, 0.723, 0.838, 2.121),
  k8 = c(0.426, 0.632, 0.753, 0.966, 1.472, 11.198),
  k9 = c(0.422, 0.605, 0.702, 0.807, 1.094, 3.733),
  k10 = c(0.431, 0.643, 0.768, 0.987, 1.508, 3.839),
  k11 = c(0.431, 0.643, 0.768, 0.987, 1.508, 3.839),
  k12 = c(0.431, 0.643, 0.768, 0.987, 1.479, 3.597),
  k13 = c(0.422, 0.606, 0.703, 0.846, 1.082, 1.769),
  k14 = c(0.188, 0.22, 0.238, 0.268, 0.331, 0.601),
  k15 = c(0.412, 0.603, 0.713, 0.904, 1.341, 3.123),
  k16 = c(0.431, 0.642, 0.766, 0.983, 1.487, 3.66),
  k17 = c(0.423, 0.622, 0.737, 0.931, 1.361, 2.96),
  k18 = c(0.405, 0.555, 0.627, 0.726, 0.841, 0.685),
  k19 = c(0.405, 0.555, 0.627, 0.726, 0.841, 0.685)
)

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = 'rho', variable.name = 'Estimator', value.name = 'MSE')

# Create the grouped bar plot
mse_plot_n100_p3 <- ggplot(data_long, aes(x = Estimator, y = MSE, fill = factor(rho))) +
  geom_bar(stat = "identity", position = "dodge") +  # Group bars by rho
  scale_fill_brewer(palette = "Set3") +  # Use a distinct color palette
  labs(title = " MSE  (n = 100, p = 3)",
       x = "Estimator", y = "Mean Squared Error (MSE)", fill = expression(rho)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title = element_text(size = 10),
        plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))

# plot for coverage probability n = 100, p = 3 , s = 1

# Create the data frame based on Table 14
data <- data.frame(
  rho = c(0.60, 0.80, 0.85, 0.90, 0.95, 0.99),
  OLS = c(0.952, 0.955, 0.957, 0.956, 0.955, 0.954),
  k1 = c(0.938, 0.871, 0.417, 0.671, 0.427, 0.141),
  k2 = c(0.94, 0.914, 0.676, 0.847, 0.752, 0.606),
  k3 = c(0.906, 0.636, 0.041, 0.305, 0.109, 0.005),
  k4 = c(0.901, 0.818, 0.262, 0.709, 0.594, 0.454),
  k5 = c(0.062, 0.062, 0.0, 0.0, 0.124, 0.191),
  k6 = c(0.94, 0.921, 0.595, 0.867, 0.781, 0.634),
  k7 = c(0.941, 0.901, 0.076, 0.818, 0.664, 0.058),
  k8 = c(0.952, 0.952, 0.952, 0.954, 0.955, 0.954),
  k9 = c(0.94, 0.914, 0.639, 0.846, 0.755, 0.605),
  k10 = c(0.952, 0.955, 0.957, 0.956, 0.955, 0.954),
  k11 = c(0.952, 0.955, 0.957, 0.956, 0.955, 0.954),
  k12 = c(0.951, 0.955, 0.954, 0.953, 0.951, 0.948),
  k13 = c(0.942, 0.917, 0.395, 0.852, 0.753, 0.587),
  k14 = c(0, 0, 0.004, 0.005, 0.046, 0.215),
  k15 = c(0.906, 0.905, 0.942, 0.904, 0.895, 0.872),
  k16 = c(0.951, 0.954, 0.954, 0.954, 0.944, 0.944),
  k17 = c(0.939, 0.936, 0.931, 0.927, 0.908, 0.879),
  k18 = c(0.934, 0.9, 0.879, 0.826, 0.671, 0.042),
  k19 = c(0.934, 0.9, 0.879, 0.826, 0.671, 0.042)
)

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = 'rho', variable.name = 'Estimator', value.name = 'CoverageProbability')

# Create the line plot
coverage_prob_plot_n100_p3 <-ggplot(data_long, aes(x = rho, y = CoverageProbability, color = Estimator)) +
  geom_point(size = 3) +                            # Add points
  geom_line(aes(group = Estimator), linetype = "dashed", size = 0.8) +  # Add dashed lines
  labs(title = "Coverage Probability (n = 100, p = 3)",
       x = expression(rho), y = "Coverage Probability") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),  
        axis.title = element_text(size = 10),
        plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))

# plot for CI width n = 100, p = 3 , s = 1

# Create the data frame based on Table 15
data <- data.frame(
  rho = c(0.60, 0.80, 0.85, 0.90, 0.95, 0.99),
  OLS = c(0.431, 0.643, 0.768, 0.987, 1.508, 3.841),
  k1 = c(0.42, 0.584, 0.649, 0.701, 0.673, 1.19),
  k2 = c(0.421, 0.604, 0.701, 0.845, 1.09, 4.87),
  k3 = c(0.404, 0.476, 0.475, 0.445, 0.335, 0.403),
  k4 = c(0.404, 0.549, 0.616, 0.704, 0.831, 3.062),
  k5 = c(0.195, 0.224, 0.245, 0.281, 0.356, 1.617),
  k6 = c(0.424, 0.614, 0.718, 0.885, 1.206, 8.694),
  k7 = c(0.409, 0.557, 0.627, 0.723, 0.838, 2.121),
  k8 = c(0.426, 0.632, 0.753, 0.966, 1.472, 11.198),
  k9 = c(0.422, 0.605, 0.702, 0.807, 1.094, 3.733),
  k10 = c(0.431, 0.643, 0.768, 0.987, 1.508, 3.839),
  k11 = c(0.431, 0.643, 0.768, 0.987, 1.508, 3.839),
  k12 = c(0.431, 0.643, 0.768, 0.987, 1.479, 3.597),
  k13 = c(0.422, 0.606, 0.703, 0.846, 1.082, 1.769),
  k14 = c(0.188, 0.22, 0.238, 0.268, 0.331, 0.601),
  k15 = c(0.412, 0.603, 0.713, 0.904, 1.341, 3.123),
  k16 = c(0.431, 0.642, 0.766, 0.983, 1.487, 3.66),
  k17 = c(0.423, 0.622, 0.737, 0.931, 1.361, 2.96),
  k18 = c(0.405, 0.555, 0.627, 0.726, 0.841, 0.685),
  k19 = c(0.405, 0.555, 0.627, 0.726, 0.841, 0.685)
)

# Reshape the data to long format for ggplot
data_long <- melt(data, id.vars = 'rho', variable.name = 'Estimator', value.name = 'CI_Width')

# Create the grouped bar plot
ci_width_plot_n100_p3 <- ggplot(data_long, aes(x = Estimator, y = CI_Width, fill = factor(rho))) +
  geom_bar(stat = "identity", position = "dodge") +  # Group bars by rho
  scale_fill_brewer(palette = "Set3") +  # Use a distinct color palette
  labs(title = "Confidence Interval Width (n = 100, p = 3)",
       x = "Estimator", y = "Confidence Interval Width", fill = expression(rho)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),  
        axis.title = element_text(size = 10),
        plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))

# # Now remove the legends from all individual plots
# mse_plot_n30_p3 <- mse_plot_n30_p3 + theme(legend.position = "left")
# mse_plot_n100_p3 <- mse_plot_n100_p3 + theme(legend.position = "none")
# coverage_prob_plot_n30_p3 <- coverage_prob_plot_n30_p3 + theme(legend.position = "none")
# coverage_prob_plot_n100_p3 <- coverage_prob_plot_n100_p3 + theme(legend.position = "left")
# ci_width_plot_n30_p3 <- ci_width_plot_n30_p3 + theme(legend.position = "")
# ci_width_plot_n100_p3 <- ci_width_plot_n100_p3 + theme(legend.position = "none")

# Open a JPEG device to save the plot
jpeg("final_plot_with_single_legend.jpeg", width = 1800, height = 1600, res = 150)

# Arrange the plots in a 3x2 grid and add the legend separately
grid.arrange(
  mse_plot_n30_p3, mse_plot_n100_p3,
  coverage_prob_plot_n30_p3, coverage_prob_plot_n100_p3,
  ci_width_plot_n30_p3, ci_width_plot_n100_p3,
  # Add the legend here as a separate element
  ncol = 2, nrow = 3,  # One extra row for the legend
  heights = c(1.3, 1.3, 1.3),
  widths = c(1.3, 1.3))# The last row height for the legend

# Close the device to save the plot
dev.off()

```

### 2024-10-01 plots.qmd
data correction

@@
   rho = c(0.60, 0.80, 0.85, 0.90, 0.95, 0.99),
-  OLS = c(0.19, 0.359, 0.479, 0.73, 1.521, 9.75),
-  k1 = c(0.214, 0.412, 0.518, 0.675, 0.941, 8.486),
-  k2 = c(0.207, 0.376, 0.474, 0.648, 0.875, 38.301),
-  k3 = c(0.283, 0.494, 0.58, 0.687, 0.825, 1.543),
-  k4 = c(0.237, 0.401, 0.483, 0.612, 0.904, 21.909),
-  k5 = c(0.598, 0.697, 0.734, 0.79, 0.909, 9.19),
-  k6 = c(0.202, 0.38, 0.494, 0.708, 1.329, 72.98),
-  k7 = c(0.174, 0.314, 0.396, 0.524, 0.737, 1.877),
-  k8 = c(0.176, 0.324, 0.428, 0.642, 1.309, 62.724),
-  k9 = c(0.207, 0.375, 0.473, 0.648, 1.107, 67.02),
-  k10 = c(0.19, 0.359, 0.479, 0.73, 1.52, 75.52),
-  k11 = c(0.19, 0.359, 0.479, 0.73, 1.521, 75.668),
-  k12 = c(0.192, 0.361, 0.481, 0.714, 1.439, 67.185),
-  k13 = c(0.216, 0.383, 0.473, 0.618, 0.946, 22.87),
-  k14 = c(0.6, 0.64, 0.658, 0.689, 0.77, 8.675),
-  k15 = c(0.218, 0.363, 0.458, 0.644, 1.187, 48.062),
-  k16 = c(0.191, 0.36, 0.478, 0.719, 1.464, 69.634),
-  k17 = c(0.2, 0.35, 0.447, 0.63, 1.134, 37.093),
-  k18 = c(0.191, 0.34, 0.423, 0.552, 0.758, 1.285),
-  k19 = c(0.191, 0.34, 0.423, 0.552, 0.758, 1.285)
+  OLS = c(0.19, 0.359, 0.479, 0.73, 1.521, 8.408),
+  k1 = c(0.214, 0.412, 0.518, 0.675, 0.941, 1.658),
+  k2 = c(0.207, 0.376, 0.474, 0.648, 1.107, 4.604),
+  k3 = c(0.283, 0.494, 0.58, 0.687, 0.825, 0.989),
+  k4 = c(0.237, 0.401, 0.483, 0.612, 0.904, 2.896),
+  k5 = c(0.598, 0.697, 0.734, 0.79, 0.909, 1.687),
+  k6 = c(0.202, 0.38, 0.494, 0.708, 1.329, 7.336),
+  k7 = c(0.174, 0.314, 0.396, 0.524, 0.737, 0.996),
+  k8 = c(0.176, 0.324, 0.428, 0.642, 1.309, 6.978),
+  k9 = c(0.207, 0.375, 0.473, 0.648, 1.107, 4.61),
+  k10 = c(0.19, 0.359, 0.479, 0.73, 1.52, 8.393),
+  k11 = c(0.19, 0.359, 0.479, 0.73, 1.521, 8.408),
+  k12 = c(0.192, 0.361, 0.478, 0.714, 1.439, 7.554),
+  k13 = c(0.216, 0.383, 0.473, 0.618, 0.946, 2.995),
+  k14 = c(0.6, 0.64, 0.658, 0.689, 0.77, 1.544),
+  k15 = c(0.218, 0.363, 0.458, 0.644, 1.187, 5.493),
+  k16 = c(0.191, 0.36, 0.478, 0.719, 1.464, 7.802),
+  k17 = c(0.2, 0.35, 0.447, 0.63, 1.134, 4.362),
+  k18 = c(0.191, 0.34, 0.423, 0.552, 0.758, 0.992),
+  k19 = c(0.191, 0.34, 0.423, 0.552, 0.758, 0.992)
 )
@@
   k2 = c(0.887, 0.793, 0.752, 0.697, 0.639, 0.711),
-  k3 = c(0.733, 0.454, 0.436, 0.25, 0.133, 0.024),
+  k3 = c(0.733, 0.454, 0.36, 0.25, 0.133, 0.024),
   k4 = c(0.788, 0.649, 0.603, 0.546, 0.483, 0.489),
-  k5 = c(0.202, 0.174, 0.177, 0.181, 0.197, 0.197),
+  k5 = c(0.202, 0.174, 0.177, 0.181, 0.197, 0.267),
   k6 = c(0.916, 0.852, 0.814, 0.75, 0.676, 0.797),
@@
   k11 = c(0.953, 0.957, 0.956, 0.956, 0.953, 0.953),
-  k12 = c(0.945, 0.928, 0.914, 0.9, 0.527, 0.9),
-  k13 = c(0.854, 0.726, 0.674, 0.611, 0.502, 0.611),
-  k14 = c(0.05, 0.092, 0.121, 0.164, 0.227, 0.215),
-  k15 = c(0.871, 0.847, 0.832, 0.81, 0.794, 0.933),
-  k16 = c(0.947, 0.935, 0.926, 0.915, 0.941, 0.944),
-  k17 = c(0.91, 0.875, 0.857, 0.826, 0.811, 0.737),
-  k18 = c(0.879, 0.736, 0.65, 0.479, 0.174, 0.737),
-  k19 = c(0.879, 0.736, 0.65, 0.479, 0.174, 0.737)
+  k12 = c(0.945, 0.928, 0.914, 0.9, 0.903, 0.933),
+  k13 = c(0.854, 0.726, 0.674, 0.611, 0.527, 0.502),
+  k14 = c(0.05, 0.092, 0.121, 0.164, 0.227, 0.309),
+  k15 = c(0.871, 0.847, 0.832, 0.81, 0.794, 0.81),
+  k16 = c(0.947, 0.935, 0.926, 0.915, 0.921, 0.941),
+  k17 = c(0.91, 0.875, 0.857, 0.826, 0.8, 0.811),
+  k18 = c(0.879, 0.736, 0.65, 0.479, 0.174, 0),
+  k19 = c(0.879, 0.736, 0.65, 0.479, 0.174, 0)
 )
@@
   k3 = c(0.677, 0.641, 0.608, 0.551, 0.454, 0.309),
-  k4 = c(0.724, 0.838, 0.889, 0.931, 1.163, 7.252),
-  k5 = c(0.39, 0.427, 0.451, 0.492, 0.592, 0.935),
-  k6 = c(0.861, 1.147, 1.29, 1.515, 2.035, 3.483),
-  k7 = c(0.782, 0.906, 0.94, 0.956, 0.586, 2.331),
-  k8 = c(0.88, 1.275, 1.158, 1.923, 2.902, 2.633),
-  k9 = c(0.827, 1.052, 1.158, 1.923, 2.699, 2.635),
+  k4 = c(0.724, 0.838, 0.889, 0.931, 1.163, 2.197),
+  k5 = c(0.39, 0.427, 0.451, 0.492, 0.592, 1.092),
+  k6 = c(0.861, 1.147, 1.29, 1.515, 2.035, 5.278),
+  k7 = c(0.782, 0.906, 0.94, 0.956, 0.586, 0.586),
+  k8 = c(0.88, 1.275, 1.158, 1.923, 2.902, 7.252),
+  k9 = c(0.827, 1.052, 1.158, 1.923, 2.699, 3.509),
   k10 = c(0.923, 1.364, 1.535, 2.084, 3.175, 8.052),
-  k11 = c(0.923, 1.364, 1.535, 2.084, 3.175, 8.052),
+  k11 = c(0.923, 1.364, 1.535, 2.084, 3.175, 8.117),
   k12 = c(0.907, 1.302, 1.522, 1.893, 2.737, 6.459),
@@
   k15 = c(0.807, 1.115, 1.29, 1.572, 2.208, 4.949),
-  k16 = c(0.912, 1.132, 1.517, 1.943, 2.845, 6.623),
+  k16 = c(0.912, 1.132, 1.517, 1.943, 2.845, 6.823),
   k17 = c(0.839, 1.15, 1.317, 1.754, 2.175, 4.013),
-  k18 = c(0.732, 0.833, 0.855, 0.854, 0.771, 0.485),
-  k19 = c(0.732, 0.833, 0.855, 0.854, 0.771, 0.485)
+  k18 = c(0.732, 0.833, 0.855, 0.854, 0.771, 0.488),
+  k19 = c(0.732, 0.833, 0.855, 0.854, 0.771, 0.488)
 )
@@
   rho = c(0.60, 0.80, 0.85, 0.90, 0.95, 0.99),
-  OLS = c(0.431, 0.643, 0.768, 0.987, 1.508, 3.841),
-  k1 = c(0.42, 0.584, 0.649, 0.701, 0.673, 1.19),
-  k2 = c(0.421, 0.604, 0.701, 0.845, 1.09, 4.87),
-  k3 = c(0.404, 0.476, 0.475, 0.445, 0.335, 0.403),
-  k4 = c(0.404, 0.549, 0.616, 0.704, 0.831, 3.062),
-  k5 = c(0.195, 0.224, 0.245, 0.281, 0.356, 1.617),
-  k6 = c(0.424, 0.614, 0.718, 0.885, 1.206, 8.694),
-  k7 = c(0.409, 0.557, 0.627, 0.723, 0.838, 2.121),
-  k8 = c(0.426, 0.632, 0.753, 0.966, 1.472, 11.198),
-  k9 = c(0.422, 0.605, 0.702, 0.807, 1.094, 3.733),
-  k10 = c(0.431, 0.643, 0.768, 0.987, 1.508, 3.839),
-  k11 = c(0.431, 0.643, 0.768, 0.987, 1.508, 3.839),
-  k12 = c(0.431, 0.643, 0.768, 0.987, 1.479, 3.597),
-  k13 = c(0.422, 0.606, 0.703, 0.846, 1.082, 1.769),
-  k14 = c(0.188, 0.22, 0.238, 0.268, 0.331, 0.601),
-  k15 = c(0.412, 0.603, 0.713, 0.904, 1.341, 3.123),
-  k16 = c(0.431, 0.642, 0.766, 0.983, 1.487, 3.66),
-  k17 = c(0.423, 0.622, 0.737, 0.931, 1.361, 2.96),
-  k18 = c(0.405, 0.555, 0.627, 0.726, 0.841, 0.685),
-  k19 = c(0.405, 0.555, 0.627, 0.726, 0.841, 0.685)
+  OLS = c(0.047,0.089,0.119,0.181,0.377,2.079),
+  k1 = c(0.049,0.107,0.158,0.268,0.518,1.005),
+  k2 = c(0.049,0.097,0.132,0.203,0.393),
+  k3 = c(0.059,0.173,0.264,0.413,0.658,0.944),
+  k4 = c(0.055,0.115,0.158,0.24,0.419,1.075),
+  k5 = c(0.53,0.604,0.632,0.661,0.722,0.983),
+  k6 = c(0.049,0.096,0.131,0.202,0.404,1.761),
+  k7 = c(0.047,0.091,0.122,0.186,0.352,0.825),
+  k8 = c(0.047,0.087,0.116,0.176,0.364,1.985),
+  k9 = c(0.049,0.096,0.131,0.203,0.393,1.397),
+  k10 = c(0.047,0.089,0.119,0.181,0.377,2.079),
+  k11 = c(0.047, 0.089,0.119,0.181,0.377,2.079),
+  k12 = c(0.047,0.09,0.12,0.182,0.378,2.039),
+  k13 = c(0.049,0.096,0.13,0.202,0.39,1.327),
+  k14 = c(0.565, 0.582,0.591,0.609,0.647,0.831),
+  k15 = c(0.06,0.103,0.13,0.192,0.37,1.763),
+  k16 = c(0.047,0.09,0.12,0.182,0.378,2.052),
+  k17 = c(0.05,0.092,0.121,0.184,0.366,1.698),
+  k18 = c(0.048,0.092,0.123,0.185,0.351,0.827),
+  k19 = c(0.048,0.092,0.123,0.185,0.351,0.827)
 )
@@
   OLS = c(0.431, 0.643, 0.768, 0.987, 1.508, 3.841),
-  k1 = c(0.42, 0.584, 0.649, 0.701, 0.673, 1.19),
-  k2 = c(0.421, 0.604, 0.701, 0.845, 1.09, 4.87),
-  k3 = c(0.404, 0.476, 0.475, 0.445, 0.335, 0.403),
-  k4 = c(0.404, 0.549, 0.616, 0.704, 0.831, 3.062),
-  k5 = c(0.195, 0.224, 0.245, 0.281, 0.356, 1.617),
-  k6 = c(0.424, 0.614, 0.718, 0.885, 1.206, 8.694),
-  k7 = c(0.409, 0.557, 0.627, 0.723, 0.838, 2.121),
-  k8 = c(0.426, 0.632, 0.753, 0.966, 1.472, 11.198),
-  k9 = c(0.422, 0.605, 0.702, 0.807, 1.094, 3.733),
-  k10 = c(0.431, 0.643, 0.768, 0.987, 1.508, 3.839),
-  k11 = c(0.431, 0.643, 0.768, 0.987, 1.508, 3.839),
-  k12 = c(0.431, 0.643, 0.768, 0.987, 1.479, 3.597),
+  k1 = c(0.42, 0.584, 0.649, 0.701, 0.673, 0.494),
+  k2 = c(0.421, 0.604, 0.701, 0.845, 1.09, 1.874),
+  k3 = c(0.404, 0.476, 0.475, 0.445, 0.335, 0.159),
+  k4 = c(0.404, 0.549, 0.616, 0.704, 0.831, 1.236),
+  k5 = c(0.195, 0.224, 0.245, 0.281, 0.356, 0.602),
+  k6 = c(0.424, 0.614, 0.718, 0.885, 1.206, 2.339),
+  k7 = c(0.409, 0.557, 0.627, 0.723, 0.838, 0.708),
+  k8 = c(0.426, 0.632, 0.753, 0.966, 1.472, 3.733),
+  k9 = c(0.422, 0.605, 0.702, 0.807, 1.094, 1.883),
+  k10 = c(0.431, 0.643, 0.768, 0.987, 1.508, 3.893),
+  k11 = c(0.431, 0.643, 0.768, 0.987, 1.508, 3.841),
+  k12 = c(0.431, 0.643, 0.765, 0.981, 1.479, 3.597),
   k13 = c(0.422, 0.606, 0.703, 0.846, 1.082, 1.769),
-  k14 = c(0.188, 0.22, 0.238, 0.268, 0.331, 0.601),
+  k14 = c(0.188, 0.22, 0.238, 0.268, 0.331, 0.58),
   k15 = c(0.412, 0.603, 0.713, 0.904, 1.341, 3.123),

### 2024-10-02 plots.qmd
updater plots

@@
 ```{r}
-
 # Load necessary libraries
@@
 # Reshape the data to long format for ggplot
-data_long <- melt(data, id.vars = 'rho', variable.name = 'Estimator', value.name = 'MSE')
+data_long <- melt(data, id.vars = "rho", variable.name = "Estimator", value.name = "MSE")
 
 # Create the grouped bar plot
-mse_plot_n30_p3 <-ggplot(data_long, aes(x = Estimator, y = MSE, fill = factor(rho))) +
+mse_plot_n30_p3 <- ggplot(data_long, aes(x = Estimator, y = MSE, fill = factor(rho))) +
   geom_bar(stat = "identity", position = "dodge") + # Group bars by rho
   scale_fill_brewer(palette = "Set3") + # Use a distinct color palette
-  labs(title = "MSE (n = 30, p = 3)",
-       x = "Estimator", y = "Mean Squared Error (MSE)", fill = expression(rho)) +
+  labs(
+    title = "MSE (n = 30, p = 3)",
+    x = "Estimator", y = "Mean Squared Error (MSE)", fill = expression(rho)
+  ) +
   theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),  
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
     axis.title = element_text(size = 10),
-        plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))
+    plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm")
+  )
 
@@
 # Reshape the data to long format for ggplot
-data_long <- melt(data, id.vars = 'rho', variable.name = 'Estimator', value.name = 'CoverageProbability')
+data_long <- melt(data, id.vars = "rho", variable.name = "Estimator", value.name = "CoverageProbability")
 
@@
   geom_line(aes(group = Estimator), linetype = "dashed", size = 0.8) + # Add dashed lines
-  labs(title = "Coverage Probability (n = 30, p = 3)",
-       x = expression(rho), y = "Coverage Probability") +
+  labs(
+    title = "Coverage Probability (n = 30, p = 3)",
+    x = expression(rho), y = "Coverage Probability"
+  ) +
   theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8),  
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
     axis.title = element_text(size = 10),
-        plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))
+    plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm")
+  )
 
@@
 # Reshape the data to long format for ggplot
-data_long <- melt(data, id.vars = 'rho', variable.name = 'Estimator', value.name = 'CI_Width')
+data_long <- melt(data, id.vars = "rho", variable.name = "Estimator", value.name = "CI_Width")
 
@@
   scale_fill_brewer(palette = "Set3") + # Use a distinct color palette
-  labs(title = "Confidence Interval Width (n = 30, p = 3)",
-       x = "Estimator", y = "Confidence Interval Width", fill = expression(rho)) +
+  labs(
+    title = "Confidence Interval Width (n = 30, p = 3)",
+    x = "Estimator", y = "Confidence Interval Width", fill = expression(rho)
+  ) +
   theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),   axis.title = element_text(size = 10),
-  plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1), axis.title = element_text(size = 10),
+    plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm")
+  )
 
@@
 
-# Create the data frame based on Table 15 (MSE values)
 data <- data.frame(
   rho = c(0.60, 0.80, 0.85, 0.90, 0.95, 0.99),
-  OLS = c(0.047,0.089,0.119,0.181,0.377,2.079),
-  k1 = c(0.049,0.107,0.158,0.268,0.518,1.005),
-  k2 = c(0.049,0.097,0.132,0.203,0.393),
-  k3 = c(0.059,0.173,0.264,0.413,0.658,0.944),
-  k4 = c(0.055,0.115,0.158,0.24,0.419,1.075),
-  k5 = c(0.53,0.604,0.632,0.661,0.722,0.983),
-  k6 = c(0.049,0.096,0.131,0.202,0.404,1.761),
-  k7 = c(0.047,0.091,0.122,0.186,0.352,0.825),
-  k8 = c(0.047,0.087,0.116,0.176,0.364,1.985),
-  k9 = c(0.049,0.096,0.131,0.203,0.393,1.397),
-  k10 = c(0.047,0.089,0.119,0.181,0.377,2.079),
-  k11 = c(0.047, 0.089,0.119,0.181,0.377,2.079),
-  k12 = c(0.047,0.09,0.12,0.182,0.378,2.039),
-  k13 = c(0.049,0.096,0.13,0.202,0.39,1.327),
-  k14 = c(0.565, 0.582,0.591,0.609,0.647,0.831),
-  k15 = c(0.06,0.103,0.13,0.192,0.37,1.763),
-  k16 = c(0.047,0.09,0.12,0.182,0.378,2.052),
-  k17 = c(0.05,0.092,0.121,0.184,0.366,1.698),
-  k18 = c(0.048,0.092,0.123,0.185,0.351,0.827),
-  k19 = c(0.048,0.092,0.123,0.185,0.351,0.827)
+  OLS = c(0.047, 0.089, 0.119, 0.181, 0.377, 2.079),
+  k1 = c(0.049, 0.107, 0.158, 0.268, 0.518, 1.005),
+  k2 = c(0.049, 0.097, 0.132, 0.203, 0.393, 1.396),
+  k3 = c(0.059, 0.173, 0.264, 0.413, 0.658, 0.944),
+  k4 = c(0.055, 0.115, 0.158, 0.24, 0.419, 1.075),
+  k5 = c(0.53, 0.604, 0.632, 0.661, 0.722, 0.983),
+  k6 = c(0.049, 0.096, 0.131, 0.202, 0.404, 1.761),
+  k7 = c(0.047, 0.091, 0.122, 0.186, 0.352, 0.825),
+  k8 = c(0.047, 0.087, 0.116, 0.176, 0.364, 1.985),
+  k9 = c(0.049, 0.096, 0.131, 0.203, 0.393, 1.397),
+  k10 = c(0.047, 0.089, 0.119, 0.181, 0.377, 2.079),
+  k11 = c(0.047, 0.089, 0.119, 0.181, 0.377, 2.079),
+  k12 = c(0.047, 0.09, 0.12, 0.182, 0.378, 2.039),
+  k13 = c(0.049, 0.096, 0.13, 0.202, 0.39, 1.327),
+  k14 = c(0.565, 0.582, 0.591, 0.609, 0.647, 0.831),
+  k15 = c(0.06, 0.103, 0.13, 0.192, 0.37, 1.763),
+  k16 = c(0.047, 0.09, 0.12, 0.182, 0.378, 2.052),
+  k17 = c(0.05, 0.092, 0.121, 0.184, 0.366, 1.698),
+  k18 = c(0.048, 0.092, 0.123, 0.185, 0.351, 0.827),
+  k19 = c(0.048, 0.092, 0.123, 0.185, 0.351, 0.827)
 )
@@
 # Reshape the data to long format for ggplot
-data_long <- melt(data, id.vars = 'rho', variable.name = 'Estimator', value.name = 'MSE')
+data_long <- melt(data, id.vars = "rho", variable.name = "Estimator", value.name = "MSE")
 
@@
   scale_fill_brewer(palette = "Set3") + # Use a distinct color palette
-  labs(title = " MSE  (n = 100, p = 3)",
-       x = "Estimator", y = "Mean Squared Error (MSE)", fill = expression(rho)) +
+  labs(
+    title = " MSE  (n = 100, p = 3)",
+    x = "Estimator", y = "Mean Squared Error (MSE)", fill = expression(rho)
+  ) +
   theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
     axis.title = element_text(size = 10),
-        plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))
+    plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm")
+  )
 
@@
 # Reshape the data to long format for ggplot
-data_long <- melt(data, id.vars = 'rho', variable.name = 'Estimator', value.name = 'CoverageProbability')
+data_long <- melt(data, id.vars = "rho", variable.name = "Estimator", value.name = "CoverageProbability")
 
 # Create the line plot
-coverage_prob_plot_n100_p3 <-ggplot(data_long, aes(x = rho, y = CoverageProbability, color = Estimator)) +
+coverage_prob_plot_n100_p3 <- ggplot(data_long, aes(x = rho, y = CoverageProbability, color = Estimator)) +
   geom_point(size = 3) + # Add points
   geom_line(aes(group = Estimator), linetype = "dashed", size = 0.8) + # Add dashed lines
-  labs(title = "Coverage Probability (n = 100, p = 3)",
-       x = expression(rho), y = "Coverage Probability") +
+  labs(
+    title = "Coverage Probability (n = 100, p = 3)",
+    x = expression(rho), y = "Coverage Probability"
+  ) +
   theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),  
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
     axis.title = element_text(size = 10),
-        plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))
+    plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm")
+  )
 
+coverage_prob_plot_n100_p3
 # plot for CI width n = 100, p = 3 , s = 1
@@
   scale_fill_brewer(palette = "Set3") + # Use a distinct color palette
-  labs(title = "Confidence Interval Width (n = 100, p = 3)",
-       x = "Estimator", y = "Confidence Interval Width", fill = expression(rho)) +
+  labs(
+    title = "Confidence Interval Width (n = 100, p = 3)",
+    x = "Estimator", y = "Confidence Interval Width", fill = expression(rho)
+  ) +
   theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),  
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
     axis.title = element_text(size = 10),
-        plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm"))
+    plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm")
+  )
 
@@
 # Arrange the plots in a 3x2 grid and add the legend separately
+
+complete_plot <-
   grid.arrange(
@@
     heights = c(1.3, 1.3, 1.3),
-  widths = c(1.3, 1.3))# The last row height for the legend
+    widths = c(1.3, 1.3)
+  ) # The last row height for the legend
+
+jpeg("mse_plot.jpeg", width = 1800, height = 600, res = 150)
+
+mse_plot <-
+  grid.arrange(
+    mse_plot_n30_p3, mse_plot_n100_p3,
+    ncol = 2, nrow = 1, # One extra row for the legend
+    heights = c(1.3),
+    widths = c(1.3, 1.3)
+  ) # The last row height for the legend
+dev.off()
+
+jpeg("cp_plot.jpeg", width = 2000, height = 1000, res = 150)
+
+cp_plot <-
+  grid.arrange(
+    coverage_prob_plot_n30_p3, coverage_prob_plot_n100_p3,
+    ncol = 2, nrow = 1, # One extra row for the legend
+    heights = c(1.3),
+    widths = c(1.3, 1.3)
+  ) # The last row height for the legend
+
+dev.off()
+
+jpeg("ciw_plot.jpeg", width = 1800, height = 600, res = 150)
+
+ciw_plot <-
+  grid.arrange(
+    ci_width_plot_n30_p3, ci_width_plot_n100_p3,
+    ncol = 2, nrow = 1, # One extra row for the legend
+    heights = c(1.3),
+    widths = c(1.3, 1.3)
+  ) # The last row height for the legend
 
@@
 dev.off()
-
 ```

### 2024-10-03 draft_1.qmd

@@
 $$
+
+A brief summary of the estimated MSE, coverage probability and width of the CI for sample size n = 30, 50, 100 and number of predictors, p = 3, 10 is presented in Table 1 - Table 6.
 All computations are performed with the R Statistical Software (v4.4.0; @r_soft).
 
-***** explain something about the tables
+# Simulation Results and Discussion
 
-# Results
+A shrinkage estimator is considered to perform better overall if the estimated MSE is comparatively lower than the OLS.
+When it comes to performance based on CIs, a shrinkage estimator that maintains the nominal coverage probability under various conditions but has a narrower CI width is more desirable.
+The key conclusions obtained from the tables based on these comparison criteria is explained below,
+
+## Performance based on MSE
+
+Plot 1: Performance based on MSE
+![](mse_plot.jpeg)
+
+## Performance based on Coverage Probability
+
+Plot 2: Performance based on Coverage Probability
+![](cp_plot.jpeg)
+## Performance based on CI width
+
+Plot 3: Performance based on CI width
+![](ciw_plot.jpeg)
+
+## Table 1: MSE results for n = 30, p = 3
+## Table 2: Coverage Probability results for n = 30, p = 3
+## Table 3: Confidence Interval width results for n = 30, p = 3
+## Table 4: MSE results for n = 30, p = 10
+## Table 5: Coverage Probability results for n = 30, p = 10
+## Table 6: Confidence Interval width results for n = 30, p = 10
+
+## Table 7: MSE results for n = 50, p = 3
+## Table 8: Coverage Probability results for n = 50, p = 3
+## Table 9: Confidence Interval width results for n = 50, p = 3
+## Table 10: MSE results for n = 50, p = 10
+## Table 11: Coverage Probability results for n = 50, p = 10
+## Table 12: Confidence Interval width results for n = 50, p = 10
+
+## Table 13: MSE results for n = 100, p = 3
+## Table 14: Coverage Probability results for n = 100, p = 3
+## Table 15: Confidence Interval width results for n = 100, p = 3
+## Table 16: MSE results for n = 100, p = 10
+## Table 17: Coverage Probability results for n = 100, p = 10
+## Table 18: Confidence Interval width results for n = 100, p = 10
 

### 2024-11-04 draft_1.qmd
plots and tables

@@
 CI width = \frac{\sum_{i=1}^{5000} (\hat{\beta}_U - \hat{\beta}_L)}{5000},
-$$
-$$
+$$ $$
 CP = \frac{\#(\hat{\beta}_L < \beta < \hat{\beta}_U)}{5000},
@@
 
-Plot 1: Performance based on MSE
-![](mse_plot.jpeg)
+-   which k's perform better
+
+-   relation with n
+
+When sample size is small, compared to most of the the selected shrinkage parameters OLS has very high MSE, especially when rho is high.
+Shrinkage parameters k1, k3, k7, k14, k18, k19 perform better (Table 1) in controlling the variance.
+For example, when $\rho$ = 0.99 ($\sigma^2$ = 1) The MSE of OLS is 8.408, while k1 (@hoerl1970ridge) has 1.658 and k18, k19 proposed by @chandnew has an MSE of 0.992.
+The performance difference between OLS and regularization parameters gets smaller as sample size increases.
+OLS produces more reliable predictions on larger datasets, although shrinkage parameters have a competitive advantage when rho is high.
+Regardless, of the sample size and colliniearity some k's like k10 and k11 do not show a significantly lower MSE than OLS.
+
+Plot 1: Performance based on MSE ![](mse_plot.jpeg)
+
+-   relation with p
+
+ When the number of predictors is small, the MSE values for all methods are generally lower, with OLS performing reasonably well, especially in cases of low rho.
+However, shrinkage methods consistently outperform OLS, particularly when rho is higher.
+
+For instance, when n = 50, p = 3, and rho = 0.85:
+
+OLS has an MSE of 2.281, while k2 has an MSE of 1.283, demonstrating the superior performance of shrinkage parameters in controlling overfitting.
+
+Larger Number of Predictors (p = 10): With a higher number of predictors, the OLS method becomes more prone to overfitting, especially when rho is high.
+Shrinkage methods, particularly k2, k5, and k6, show substantial reductions in MSE by introducing regularization to counteract overfitting and multicollinearity.
+
+For instance, when n = 50, p = 10, and rho = 0.95:
+
+OLS has a high MSE of 80.548, but k2 reduces this to 41.5, and k6 further reduces it to 24.373.
 
@@
 
-Plot 2: Performance based on Coverage Probability
-![](cp_plot.jpeg)
-## Performance based on CI width
+Plot 2: Performance based on Coverage Probability ![](cp_plot.jpeg) \## Performance based on CI width
 
-Plot 3: Performance based on CI width
-![](ciw_plot.jpeg)
+Plot 3: Performance based on CI width ![](ciw_plot.jpeg)
+
+## Overall Comparison MSE vs Coverage Probability
 
 ## Table 1: MSE results for n = 30, p = 3
+
 ## Table 2: Coverage Probability results for n = 30, p = 3
+
 ## Table 3: Confidence Interval width results for n = 30, p = 3
+
 ## Table 4: MSE results for n = 30, p = 10
+
 ## Table 5: Coverage Probability results for n = 30, p = 10
+
 ## Table 6: Confidence Interval width results for n = 30, p = 10
@@
 ## Table 7: MSE results for n = 50, p = 3
+
 ## Table 8: Coverage Probability results for n = 50, p = 3
+
 ## Table 9: Confidence Interval width results for n = 50, p = 3
+
 ## Table 10: MSE results for n = 50, p = 10
+
 ## Table 11: Coverage Probability results for n = 50, p = 10
+
 ## Table 12: Confidence Interval width results for n = 50, p = 10
@@
 ## Table 13: MSE results for n = 100, p = 3
+
 ## Table 14: Coverage Probability results for n = 100, p = 3
+
 ## Table 15: Confidence Interval width results for n = 100, p = 3
+
 ## Table 16: MSE results for n = 100, p = 10
+
 ## Table 17: Coverage Probability results for n = 100, p = 10
+
 ## Table 18: Confidence Interval width results for n = 100, p = 10

### 2024-11-04 plots.qmd
plots and tables

@@
 
-jpeg("cp_plot.jpeg", width = 2000, height = 1000, res = 150)
+jpeg("cp_plot.jpeg", width = 2000, height = 800, res = 150)
 
@@
 ```
+
+## Correlation plot
+
+```{r}
+
+jpeg("cor_plot.jpeg", width = 1800, height = 600, res = 150)
+# Correlation plot
+
+x <- as.matrix(mtcars[2:11])
+
+# Install and load the corrplot package if not already installed
+if (!require(corrplot)) install.packages("corrplot")
+library(corrplot)
+
+# Assuming 'data' is your data frame with numeric variables
+# Calculate the correlation matrix
+correlation_matrix <- cor(x, use = "complete.obs")
+
+# Create a correlation plot with clustering
+corrplot(correlation_matrix, method = "color", order = "hclust",
+         addrect = 2, # Adds rectangles to emphasize clusters
+         tl.col = "black", # Text label color
+         tl.srt = 45, # Rotate text labels
+         col = colorRampPalette(c("blue", "white", "red"))(200))
+dev.off()
+
+```

### 2024-11-06 draft_1.qmd
edits

--- 2024-09-30 draft_1.qmd
@@
 CI width = \frac{\sum_{i=1}^{5000} (\hat{\beta}_U - \hat{\beta}_L)}{5000},
-$$
-$$
+$$ $$
 CP = \frac{\#(\hat{\beta}_L < \beta < \hat{\beta}_U)}{5000},
 $$
+
+A brief summary of the estimated MSE, coverage probability and width of the CI for sample size n = 30, 50, 100 and number of predictors, p = 3, 10 is presented in Table 1 - Table 6.
 All computations are performed with the R Statistical Software (v4.4.0; @r_soft).
 
-***** explain something about the tables
+# Simulation Results and Discussion
 
-# Results
+A shrinkage estimator is considered to perform better overall if the estimated MSE is comparatively lower than the OLS.
+When it comes to performance based on CIs, a shrinkage estimator that maintains the nominal coverage probability under various conditions but has a narrower CI width is more desirable.
+The key conclusions obtained from the tables based on these comparison criteria is explained below,
+
+## Performance based on MSE
+
+When sample size is small (Table 1, Table 2), compared to most of the the selected shrinkage parameters OLS has very high MSE, especially when rho is high.
+Shrinkage parameters k1, k3, k7, k14, k18, k19 perform better (Table 1) in controlling the variance.
+For example, when $\rho$ = 0.99 ($\sigma^2$ = 1) The MSE of OLS is 8.408, while k1 (@hoerl1970ridge) has 1.658 and k18, k19 proposed by @chandnew has an MSE of 0.992.
+The performance difference between OLS and regularization parameters gets smaller as sample size increases.
+OLS produces more reliable predictions on larger datasets, although shrinkage parameters have a competitive advantage when rho is high.
+Regardless, of the sample size and colliniearity some k's like k10 and k11 do not show a significantly lower MSE than OLS.
+
+Plot 1: Performance based on MSE ($\sigma = 1$) ![](mse_plot.jpeg)
+
+With the increase in number of predictor overall the MSE increases for all estimators.
+Compared to OLS the shrinkage estimator show comparatively small increase in MSE in presence of high collinearity.
+For most shrinkage parameters, the MSE is quite close to the OLS estimator when the correlation level is 0.60.
+Nevertheless, as correlation increases, the shrinkage estimator perform better overall.
+
+## Performance based on Coverage Probability
+
+Coverage probabilities tend to stray from the optimum 95% aim for smaller sample numbers, especially as correlation level increases.
+Regularization parameters k2 and k5 do better at maintaining coverage probability close to 95%.
+Although for small sample some methods does not show high coverage most likely because of the bias introduced by regularization.
+In plot 2 the coverage probability of all the parameters are plotted against the correlation level.
+From the plot we can see that, for larger sample size a coverage probability of shrinkage parameters varies a lot as the correlation level increases.
+Whereas, OLS maintains optimum coverage probability throughout all conditions.
+
+Plot 2: Performance based on Coverage Probability ($\sigma = 1$) ![](cp_plot.jpeg)
+
+k8, k9, k10, k11, k12, k15, k16  stands out with persistently higher coverage probability often approaching 0.95 and higher compared to the other k's across various conditions.
+Among them k8, k10, k11, k16 maintained coverage probability above 0.95 under all conditions.
+Even under high multicollinearity these shrinkage parameters perform robustly.
+On the other hand, k14, k18 and k19 does not perform well in terms of coverage probability in situation when large number of predictors and high correlation level.
+Regularization parameters like k5, k7 and k10 perform reasonably well however are sensitive to the increasing of noise level.
+
+## Performance based on CI width
+
+Most of the shrinkage parameters see a widening of the CI's as number of predictors increase which is an indication of the increasing difficulty in estimating parameters on more complex models.
+The confidence intervals for the majority of k-values are narrowed by larger sample sizes (e.g., n=50, 100), although the improvement is not consistent for all values.
+In plot 3 the width of CI of all the parameters are plotted against the correlation level.
+
+Plot 3: Performance based on CI width ($\sigma = 1$)
+![](ciw_plot.jpeg)
+
+The findings of the CI width show that, under most circumstances, k3, k5, k7, k14, k18 and k19 have the narrower CI width than the other CI's.
+
+## Overall Performance MSE and Coverage Probability
+
+Among the shrinkage parameters the maintain a consistent coverage probability of 95%, k8 and k16 show the narrower confidence interval regardless of the conditions.
+These two regularization parameters are consistently meet the criteria of provide considerably lower confidence intervals and maintain a coverage probability of 0.95 or above.
+K8 performs marginally better than the others in striking a balance between precision and reliability.
+
+# Table 1
+
+# Table 2
+
+# Table 3
+
+# Table 4
+
+# Table 5
+
+# Table 6
 
@@
 
+In this section, we analyse the `mcdonald` dataset  available in R under `bestglm` package and has been utilized numerous times for ridge regression research.
+This data has been created from the 1973 study on pollution done by from McDonald and Schwing.
+The dataset has a total of 60 observations for 16 variables representing different environmental and demographic factors.
+A list of the variable names and their details is given in Table 7.
+
+# Table 7: Variable Description
+
+Based on the VIF (variance inflation factor) of the predictors it is seen that there are strong evidence of multicollinearity in the data as some of the independent variables have a VIF higher than 10 (Table 8).
+Furthermore, we calculated the condition number (CN) of the standardized predictors by using the formula, $CN(\kappa) = \frac{\lambda_{\max}}{\lambda_{\min}} = 930.5641$; indicating high multicollinearity between the independent variables.
+
+# Table 8 : VIF for indenpendent variables
+
+Since multicollinearity is present in the data, Ridge regression is more suitable compared to OLS in this situation.
+For demonstration purpose we choose predictors "NOX" and "HC" as they had high VIF.
+Table 8 shows the estimated coefficient, CI and CI width of OLS and ridge regression for the shrinkage parameters that had high coverage probability in the simulation.
+
+# Table 8 :
+
+From the results (Table 8) it can be seen that among the shrinkage parameters which had high coverage probability k8 and k16 produce narrower CI's.
+
 # Discussion and Conclusion
 
-Extra:
-
-The canonical form of model @eq-1 is written as, $$ y = Z\alpha + \epsilon, $$ where, $Z = X Q$, $\alpha = (\alpha_1, \alpha_2, ..., \alpha_p) = Q^T \beta$ assuming $Q$ is a $p \times p$ orthogonal matrix such that $Q^{'}Q = I_p$, and $Q^{'}X^{'}XQ = \Lambda$, where $\Lambda =diag(\lambda_1, \lambda_2, ..., \lambda_p)$ is the orthogonal matrix that consists of the eigen values of $X^{'}X$.
-
-Then the OLS estimator is canonical form is given below,
-
-$$ \hat\alpha_{OLS} = (Z^{'}Z)^{-1}Z{'}y $$
-
-The ridge regression estimator with k as the shrinkage parameter proposed by @hoerl1970ridge for $\alpha$ is written as, $$ \hat{\alpha} (k) = (Z^TZ + kI_p)^{-1} Z^Ty = W\hat{\alpha} ;     k \geq 0$$ where, $W = [I_p + k C^{-1}]^{-1}$ is the ridge regression estimator, $k = diag(k_1, k_2,..., k_p)$ and $I_p$ is a identity matrix of order p.
-
 # Bibliography

### 2024-11-06 plots.qmd
edits

@@
 
-x <- as.matrix(mtcars[2:11])
+if (!require(bestglm)) install.packages("bestglm")
+library(bestglm)
+mc_df <- mcdonald
+mc_x <- as.matrix(mc_df[1:15])
 
@@
 # Calculate the correlation matrix
-correlation_matrix <- cor(x, use = "complete.obs")
+correlation_matrix <- cor(mc_x, use = "complete.obs")
 
